---
title: "Kit_batch_analysis_07_27_17"
author: "carriewright"
date: "7/27/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First need to load the data using the raw counts and the RPM values from miRge
```{r, echo=FALSE}
miR_counts<-read.table("/home/carrie/UMI/after_UMI_tools_Nextflex_kitcomparison/UMI_NEXTflex_and_all_kits_1000ng/All_combined_1000ng/miR.Counts.csv", header = TRUE, sep = ",") 
rownames(miR_counts)<- miR_counts$miRNA#make miRNA rownames
miR_counts<-miR_counts[,2:length(colnames(miR_counts))]#remove miRNA col
miR_counts<-miR_counts[-1,]#remove miRNA col

miR_RPMs<-read.table("/home/carrie/UMI/after_UMI_tools_Nextflex_kitcomparison/UMI_NEXTflex_and_all_kits_1000ng/All_combined_1000ng/miR.RPM.csv", header = TRUE, sep = ",")
rownames(miR_RPMs)<- miR_RPMs$miRNA#make miRNA rownames
miR_RPMs<-miR_RPMs[,2:length(colnames(miR_RPMs))]#remove miRNA col
Pheno<- read.table("/home/carrie/UMI/Pheno_1000ng_full", header = T)
pheno_all <- Pheno[-grep('deduped', Pheno$File), ]
pheno_all$Kit <- relevel(droplevels(pheno_all$Kit), ref = "NextFlex")
load("/home/carrie/UMI/All_intersect_over10RPM.rda")
