---
title: "Kit_Venndiagram_1_19_18"
author: "Carrie Wright"
date: "1/19/2018"
output: html_document
---

load the data
```{r, eval=TRUE, echo=FALSE}
library(edgeR)
library(here)
#Pheno<- read.table("/Users/carriewright/Documents/miRNA seq Projects/miRNA_kit_comparison_project/DATA_ANALYSIS/Pheno_repro_full_1_16_18_ns_kept", header = T)
Pheno<-read.table(here("Complete_data/Pheno.txt"), header = TRUE)
#miR_counts<-read.table("/home/carrie/miRge/miRge-master/Keeping_Ns_Repro_Analysis/miR.Counts.csv", header = TRUE, sep = ",") #original location
#miR_counts<-read.table("/Users/carriewright/Documents/miRNA seq Projects/miRNA_kit_comparison_project/DATA_ANALYSIS/ReproData/miR.Counts.csv", header = TRUE, sep = ",")
miR_counts<-read.table(here("/Complete_data/miR.Counts.csv"), header = TRUE, sep = ",")

rownames(miR_counts)<- miR_counts$miRNA#make miRNA rownames
miR_counts<-miR_counts[,2:length(colnames(miR_counts))]#remove miRNA col

colnames(miR_counts)<-gsub("directional_dedupped|directional_deduped", "Deduped", colnames(miR_counts))
colnames(miR_counts)<-gsub("NEXT_", "NEXTflex_", colnames(miR_counts))
miRNAtotal<-t(miR_counts[1,])#extract the total miRNA counts... in case we want them
miR_counts<-miR_counts[-1,]#remove total miRNA counts row

Pheno$File<-gsub("NEXTflex_deduped", "Deduped", Pheno$File)
Pheno$Kit<-gsub("NEXTflex_deduped", "Deduped", Pheno$Kit)
Pheno$TriplicateGroup<-gsub("NEXTflex_deduped", "Deduped", Pheno$TriplicateGroup)
Pheno$miRNAtotal <-miRNAtotal
 
identical(as.character(Pheno$File), colnames(data.frame(miR_counts))) ###Check that these match 
identical(rownames(miRNAtotal), Pheno$File)


###remove 2nd batch files
miR_counts<-miR_counts[-grep("Accur", Pheno$Batch)]
Pheno<- Pheno[-grep("Accur", Pheno$Batch),]

```
## to grab only 1microgram starting amt
```{r}
# miR_counts <- data.frame(miR_counts[which(Pheno$startingAmt == "1000")])
# Pheno <- data.frame(Pheno[which(Pheno$startingAmt == "1000"),]) 
```

###TMM Normalization

```{r, eval= FALSE, echo =FALSE}
library(edgeR)
group <-Pheno$Kit
d<-DGEList(counts = miR_counts, group = group)
miR_1000_TMM_edgeR_factors <-calcNormFactors(d, method = "TMM")
TMM <-estimateCommonDisp(miR_1000_TMM_edgeR_factors)
norm_miR_counts <-data.frame(TMM$pseudo.counts)
dim(norm_miR_counts)
```
```{r, eval = TRUE, echo = FALSE}
#Pheno$startingAmt<-paste0("starting_amt_", Pheno$startingAmt)
Pheno$startingAmt<-factor(Pheno$startingAmt)
###split the data by starting Amount
split_Kit <- list() 
for(i in Pheno$Kit) { 
  split_Kit[[i]] <- data.frame(miR_counts[which(Pheno$Kit==i)])
}
###split the pheno by starting Amount
Pheno_Kit <- list() 
for(i in Pheno$Kit) { 
  Pheno_Kit[[i]] <- data.frame(Pheno[which(Pheno$Kit==i),])
}

library(DESeq2)
Kit_norm_miR <-list()
for(i in unique(Pheno$Kit)){
  dds<-DESeqDataSetFromMatrix(countData = split_Kit[[i]], colData = Pheno[which(Pheno$Kit ==i),], design = ~ startingAmt)
  dds <- estimateSizeFactors(dds)
  Kit_norm_miR[[i]]<-data.frame(counts(dds, normalized = TRUE))
  }


```

###DESeq2
```{r, eval=TRUE,warning=FALSE, message=FALSE, echo =FALSE}
library(DESeq2)
dds<-DESeqDataSetFromMatrix(countData = miR_counts, colData = Pheno, design = ~ Kit)
dds <- estimateSizeFactors(dds)
norm_miR_counts<-data.frame(counts(dds, normalized = TRUE))
dim(norm_miR_counts)
```

```{r}
###split the normalized data by kit
split_kit <- list() 
for(i in Pheno$Kit) { 
  split_kit[[i]] <- data.frame(norm_miR_counts[which(Pheno$Kit==i)]) #raw counts
} 

#save(split_kit, Pheno, file = here("Complete_data/split_kit_1batch.rda"))
```


```{r}
###genefilter

##filter each sample individually
get_det <-function(x){sum(x>10)}#determine number of miRNAs with greater than 10 reads
detected <-lapply(norm_miR_counts, get_det)
detected <-data.frame(unlist(detected))
det_Data <- cbind(detected, Pheno$startingAmt, Pheno$Kit)
colnames(det_Data)<- c("det_indv_thresh", "startingAmt", "kit")
```

filter across
```{r}
Pheno$startingAmt <-factor(Pheno$startingAmt)
split_kit_isoData <- list()
for(i in unique(Pheno$startingAmt)) {
  for(kit in unique(Pheno$Kit)){
  split_kit_isoData[[i]][[kit]] <- data.frame(norm_miR_counts[which(Pheno$startingAmt == as.character(i) & Pheno$Kit == as.character(kit))])}
}

poverafun <- genefilter::pOverA(p = 1, A = 10)#at least 100 normalized reads in all samples of the set... 
ffun <- filterfun(poverafun)
genefilt_fun<- function(x){genefilter(x, ffun)}

thresh <-list()
for(amt in names(split_kit_isoData)){
thresh[[amt]]<-lapply(split_kit_isoData[[as.character(amt)]], genefilt_fun)}

test <-split_kit_isoData$`100`$Clontech[thresh$`100`$Clontech,]

split_amt_thresh <-list()
for(amt in names(split_kit_isoData)){
for(kit in names(split_kit_isoData[[amt]])){
 split_amt_thresh[[amt]][[kit]]<- split_kit_isoData[[amt]][[kit]][thresh[[amt]][[kit]],]}
}

thresh_number <- list()
for(amt in names(split_kit_isoData)){
for(kit in names(split_kit_isoData[[amt]])){
thresh_number[[amt]][[kit]]<- dim(split_kit_isoData[[amt]][[kit]][thresh[[amt]][[kit]],])[1]}
}

thresh_number <-data.frame(thresh_number)
colnames(thresh_number) <-c("100", "250", "500", "1000", "1500", "2000")
thresh_number$kit <- rownames(thresh_number)
thresh_number <-melt(thresh_number)
thresh_number$variable <-as.numeric(as.character(thresh_number$variable))
thresh_number<-thresh_number[-which(thresh_number$value =="0"),]
thresh_number$kit <- factor(thresh_number$kit,levels = c("Clontech", "Illumina", "NEB", "NEXTflex", "Deduped", "Fivepercent"))
```
How consistent are the results...
```{r}

library(genefilter)
library(VennDiagram)
library(reshape2)
library(ggplot2)

#filter across triplicates

thresh_number <- list()
for(amt in names(split_kit_isoData)){
for(kit in names(split_kit_isoData[[amt]])){
thresh_number[[amt]][[kit]]<- dim(split_kit_isoData[[amt]][[kit]][thresh[[amt]][[kit]],])[1]}
}

thresh_number <-data.frame(thresh_number)
colnames(thresh_number) <-c("100", "250", "500", "1000", "1500", "2000")
thresh_number$kit <- rownames(thresh_number)
to_repeat <-function(x) { rep(x,3)}
thresh_kits <-data.frame(t(thresh_number))
Clontech <-data.frame(t=unlist(lapply(thresh_kits$Clontech[1:6], to_repeat)))
Illumina<-data.frame(t=unlist(lapply(thresh_kits$Illumina[4:6], to_repeat)))
NEB<-data.frame(t=unlist(lapply(thresh_kits$NEB[1:4], to_repeat)))
NEXTflex<-data.frame(t=unlist(lapply(thresh_kits$NEXTflex[1:6], to_repeat)))
Deduped<-data.frame(t=unlist(lapply(thresh_kits$Deduped[1:6], to_repeat)))
Fivepercent<- data.frame(t=unlist(lapply(thresh_kits$Fivepercent[1:6], to_repeat)))

thresh_across_amts<-rbind(Clontech, Illumina, NEB, NEXTflex, Deduped, Fivepercent)


det_Data$det_across_thresh<-thresh_across_amts$t
det_Data$not_consistent <- ((det_Data$det_indv_thresh - as.numeric(as.character(det_Data$det_across_thresh)))/det_Data$det_indv_thresh)*100
detected <-data.frame(det_Data$kit, det_Data$startingAmt, det_Data$not_consistent)

detected$det_Data.kit<-factor(detected$det_Data.kit, levels = c("Clontech", "Illumina", "NEB", "NEXTflex", "Deduped","Fivepercent"))
detected$det_Data.startingAmt<-factor(detected$det_Data.startingAmt, levels = c("100", "250", "500", "1000", "1500","2000"))



detected$det_Data.startingAmt <-gsub("starting_amt_", "",detected$det_Data.startingAmt)
ggplot(detected, aes(x =det_Data.kit, y=det_Data.not_consistent, fill = det_Data.kit)) + geom_boxplot()+ facet_grid(.~det_Data.startingAmt)

ggplot(detected, aes(x =det_Data.startingAmt, y=det_Data.not_consistent, fill = det_Data.kit)) + geom_boxplot()+ facet_grid(.~det_Data.kit) + theme(legend.position = "none", axis.text.x = element_text(size =17, angle = 60, hjust = 1), axis.text.y = element_text(size =15, hjust = 1), axis.title=element_text(size = 20), plot.title = element_text(size = 30), strip.text.x = element_text(size = 20)) + labs( x= "Starting Amount", y = " Percentage of Inconsistently \n Detected miRNA Sequences", title = "Inconsistentcy of miRNA Detection Across Kits") +geom_smooth(method = "loess", se=TRUE, color="black", aes(group=1))


ggplot(detected, aes(x =det_Data.kit, y=det_Data.not_consistent, fill = det_Data.kit)) + geom_boxplot()





summary(lm(det_Data$not_consistent~ det_Data$kit)) #sig difference in det inconsisentency across methods
#vp_alpha <- venn.diagram(miRNA_det, fill = c("red", "white", "blue", "green"), alpha = 0.5, filename = NULL)
summary(lm(det_Data$not_consistent~ det_Data$startingAmt)) #sig difference in det inconsisentency across methods
Clontech <- det_Data[which(det_Data$kit == "Clontech"),]
summary(lm(Clontech$not_consistent~Clontech$startingAmt))#F-statistic: 4.128 on 1 and 16 DF,  p-value: 0.05913
NEB<- det_Data[which(det_Data$kit == "NEB"),]
summary(lm(NEB$not_consistent~NEB$startingAmt))
Deduped<- det_Data[which(det_Data$kit == "Deduped"),]
summary(lm(Deduped$not_consistent~Deduped$startingAmt))#F-statistic: 32.44 on 1 and 16 DF,  p-value: 3.313e-05
Fivepercent<- det_Data[which(det_Data$kit == "Fivepercent"),]
summary(lm(Fivepercent$not_consistent~Fivepercent$startingAmt))#F-statistic: 11.86 on 1 and 16 DF,  p-value: 0.003334
#grid.draw(vp_alpha);
#venn.plot <- venn.diagram(
# x = miRNA_det,
#  filename = NULL
#)
#grid.draw(venn.plot)
```


```{r}
library(genefilter)
library(VennDiagram)
library(reshape2)
library(ggplot2)
#library(venneuler)
#poverafun <- genefilter::pOverA(p = .5, A = 529)# at least 529 reads for 50% of samples
poverafun <- genefilter::pOverA(p = 1, A = 10)#at least 100 normalized reads in all samples of the set... 
#poverafun <- genefilter::pOverA(p = 1, A = 10)#at least 10 raw reads in all samples #292
#poverafun <- genefilter::pOverA(p = 1, A = 100)#at least 100 raw reads in all samples #125

ffun <- filterfun(poverafun)
genefilt_fun<- function(x){genefilter(x, ffun)}
thresh<-lapply(split_kit, genefilt_fun)

split_kit_thresh <-list()
split_kit_thresh$Clontech<-split_kit$Clontech[thresh$Clontech,]
split_kit_thresh$NEB<-split_kit$NEB[thresh$NEB,]
split_kit_thresh$NEXTflex<-split_kit$NEXTflex[thresh$NEXTflex,]
split_kit_thresh$Illumina<-split_kit$Illumina[thresh$Illumina,]
split_kit_thresh$Deduped<-split_kit$Deduped[thresh$Deduped,]
split_kit_thresh$Fivepercent<-split_kit$Fivepercent[thresh$Fivepercent,]

Clontech<-rep(dim(split_kit_thresh$Clontech)[1],18)
Illumina<-rep(dim(split_kit_thresh$Illumina)[1],9)
NEB<-rep(dim(split_kit_thresh$NEB)[1],12)
NEXTflex<-rep(dim(split_kit_thresh$NEXTflex)[1],18)
Deduped<-rep(dim(split_kit_thresh$Deduped)[1],18)
Fivepercent<-rep(dim(split_kit_thresh$Fivepercent)[1],18)
thresh_across_amts<-rbind(data.frame(t =Clontech), data.frame(t =Illumina), data.frame(t=NEB), data.frame(t=NEXTflex),data.frame(t=Deduped), data.frame(t = Fivepercent))

det_Data$det_across_thresh<-thresh_across_amts$t
det_Data$not_consistent <- ((det_Data$det_indv_thresh - det_Data$det_across_thresh)/det_Data$det_indv_thresh)*100
detected <-data.frame(det_Data$kit, det_Data$startingAmt, det_Data$not_consistent)

detected$det_Data.kit<-factor(detected$det_Data.kit, levels = c("Clontech", "Illumina", "NEB", "NEXTflex", "Deduped","Fivepercent"))
detected$det_Data.startingAmt<-factor(detected$det_Data.startingAmt, levels = c("100", "250", "500", "1000", "1500","2000"))


split_kit_thresh <- split_kit_thresh[1:5]#remove 5 % control

#doesn't include overlaps and greater than 4 expression value
Clontech<-as.vector(rownames(split_kit_thresh$Clontech))
Illumina<-as.vector(rownames(split_kit_thresh$Illumina))
NEB<-as.vector(rownames(split_kit_thresh$NEB))
NEXTflex<-as.vector(rownames(split_kit_thresh$NEXTflex))
Deduped<-as.vector(rownames(split_kit_thresh$Deduped))



detected$det_Data.startingAmt <-gsub("starting_amt_", "",detected$det_Data.startingAmt)
ggplot(detected, aes(x =det_Data.kit, y=det_Data.not_consistent, fill = det_Data.kit)) + geom_boxplot()+ facet_grid(.~det_Data.startingAmt)

ggplot(detected, aes(x =det_Data.startingAmt, y=det_Data.not_consistent, fill = det_Data.kit)) + geom_boxplot()+ facet_grid(.~det_Data.kit) + theme(legend.position = "none", axis.text.x = element_text(size =17, angle = 60, hjust = 1), axis.text.y = element_text(size =15, hjust = 1), axis.title=element_text(size = 20), plot.title = element_text(size = 30), strip.text.x = element_text(size = 20)) + labs( x= "Starting Amount", y = " Percentage of Inconsistently \n Detected miRNA Sequences", title = "Inconsistentcy of miRNA Detection Across Kits") +geom_smooth(method = "lm", se=TRUE, color="black", aes(group=1))


ggplot(detected, aes(x =det_Data.kit, y=det_Data.not_consistent, fill = det_Data.kit)) + geom_boxplot()


#miRNA_det<-list("Clontech" = Clontech, "Illumina" = Illumina, "NEB" = NEB, "NextFlex" =NEXTflex)

miRNA_det<-list("Clontech\n(N=427)" = Clontech, "Illumina\n(N=443)" = Illumina, "NEB\n(N=450)" = NEB, "NextFlex\n(N=380)" =NEXTflex, "Deduped\n(N=427)" = Deduped)


summary(lm(det_Data$not_consistent~ det_Data$kit)) #sig difference in det inconsisentency across methods
#vp_alpha <- venn.diagram(miRNA_det, fill = c("red", "white", "blue", "green"), alpha = 0.5, filename = NULL)
summary(lm(det_Data$not_consistent~ det_Data$startingAmt)) #sig difference in det inconsisentency across methods
Clontech <- det_Data[which(det_Data$kit == "Clontech"),]
summary(lm(Clontech$not_consistent~Clontech$startingAmt))#F-statistic: 4.128 on 1 and 16 DF,  p-value: 0.05913
NEB<- det_Data[which(det_Data$kit == "NEB"),]
summary(lm(NEB$not_consistent~NEB$startingAmt))
Deduped<- det_Data[which(det_Data$kit == "Deduped"),]
summary(lm(Deduped$not_consistent~Deduped$startingAmt))#F-statistic: 32.44 on 1 and 16 DF,  p-value: 3.313e-05
Fivepercent<- det_Data[which(det_Data$kit == "Fivepercent"),]
summary(lm(Fivepercent$not_consistent~Fivepercent$startingAmt))#F-statistic: 11.86 on 1 and 16 DF,  p-value: 0.003334
#grid.draw(vp_alpha);
#venn.plot <- venn.diagram(
# x = miRNA_det,
#  filename = NULL
#)
#grid.draw(venn.plot)
```




VennDiagram
```{r}

gg_color_hue <- function(n) {
  hues = seq(15, 375, length = n + 1)
  hcl(h = hues, l = 65, c = 100)[1:n]
}

n = 5
cols = gg_color_hue(n)
cols <-cols[1:5]
vp_alpha <- venn.diagram(miRNA_det, fill = c(cols), alpha = 0.5, filename = NULL, margin = 0.2, cat.dist = c(.3,.3,.3, .3, .3))


grid.draw(vp_alpha);

#dev.new(width = 4, height = 4)
#plot(1:n, pch = 16, cex = 2, col = cols)
```

Need to run grid.draw(vp_alpha) seperately



Characterize the unique miRNAs for each kit

Use the fasta file in documents..
```{r}
library(here)
library(Biostrings)
seqs = readRNAStringSet(here("mature_hsa.fa"))
#hmmm ignored several sequences
newnames<-sapply(strsplit(names(seqs), " "), `[`, 1) #just to grab the first object
names(seqs)<-newnames
Clontec_seqs <-seqs[which(names(seqs) %in% rownames(split_kit_thresh$Clontech)),]
```
###might want to convert our synthetic CDNA data into RNA and vice versa here... did not find a package to do this... FastUtils is working on it... I guess I can just gsub... strange that they haven't finished- maybe I should contact

```{r}
#To grab unique sequeces for each kit look inside overlaps list to find those that correspond to the unique sequneces for each kit
vennlists<- calculate.overlap(x = miRNA_det)
vennlengths<-lapply(vennlists, length)
uniqueNEXTflex<-vennlists$a4 #NEXTflex
uniqueNEB<-vennlists$a3#NEB
uniqueIllumina <-vennlists$a2
uniqueClontech<-vennlists$a1 #Clontech
uniqueDeduped<-vennlists$a5
##checkingit
getUniqueClontech <-rownames(split_kit_thresh$Clontech)[which(!rownames(split_kit_thresh$Clontech) %in% rownames(split_kit_thresh$NEB))]
getUniqueClontech <-getUniqueClontech[which(!getUniqueClontech %in% rownames(split_kit_thresh$NEXTflex))]
getUniqueClontech <-getUniqueClontech[which(!getUniqueClontech %in% rownames(split_kit_thresh$Deduped))]
getUniqueClontech <-getUniqueClontech[which(!getUniqueClontech %in% rownames(split_kit_thresh$Illumina))]
length(getUniqueClontech)                                                               
identical(getUniqueClontech, uniqueClontech)


getUniqueIllumina<-rownames(split_kit_thresh$Illumina)[which(!rownames(split_kit_thresh$Illumina) %in% rownames(split_kit_thresh$NEB))]
getUniqueIllumina <-getUniqueIllumina[which(!getUniqueIllumina %in% rownames(split_kit_thresh$NEXTflex))]
getUniqueIllumina <-getUniqueIllumina[which(!getUniqueIllumina %in% rownames(split_kit_thresh$Deduped))]
getUniqueIllumina <-getUniqueIllumina[which(!getUniqueIllumina %in% rownames(split_kit_thresh$Clontech))]
length(getUniqueIllumina)                                                               
identical(getUniqueIllumina, uniqueIllumina)

getUniqueDeduped<-rownames(split_kit_thresh$Deduped)[which(!rownames(split_kit_thresh$Deduped) %in% rownames(split_kit_thresh$NEB))]
getUniqueDeduped <-getUniqueDeduped[which(!getUniqueDeduped %in% rownames(split_kit_thresh$NEXTflex))]
getUniqueDeduped <-getUniqueDeduped[which(!getUniqueDeduped %in% rownames(split_kit_thresh$Illumina))]
getUniqueDeduped <-getUniqueDeduped[which(!getUniqueDeduped %in% rownames(split_kit_thresh$Clontech))]
length(getUniqueDeduped)    
identical(getUniqueDeduped, uniqueDeduped)

getUniqueNEXTflex<-rownames(split_kit_thresh$NEXTflex)[which(!rownames(split_kit_thresh$NEXTflex) %in% rownames(split_kit_thresh$NEB))]
getUniqueNEXTflex <-getUniqueNEXTflex[which(!getUniqueNEXTflex %in% rownames(split_kit_thresh$Illumina))]
getUniqueNEXTflex <-getUniqueNEXTflex[which(!getUniqueNEXTflex %in% rownames(split_kit_thresh$Deduped))]
getUniqueNEXTflex <-getUniqueNEXTflex[which(!getUniqueNEXTflex %in% rownames(split_kit_thresh$Clontech))]
length(getUniqueNEXTflex)                                                               
identical(getUniqueNEXTflex, uniqueNEXTflex)

# vennlists<- calculate.overlap(x = miRNA_det)
# lapply(vennlists, length)
# uniqueNEXTflex<-vennlists[which(vennlengths == 22)] #a4 which is 28th 4th
# uniqueNEB<-vennlists[which(vennlengths == 95)] #a3 which is 29th 3rd
# which(vennlengths == 3) # Illumina # not sure which think 30th which is a2 - it is! - 2nd
# uniqueClontech<-vennlists[which(vennlengths == 18)] #a1 - the 31st  - first
# which(vennlengths == 1) #NEXTflex_deduped # not sure which think 27th which is a5 - fifth

#So the unique miRNAs are in the first five of the overlap output based on their order in the names of the list miRNA_det input
```


###

Grab unique lists
```{r}
names(miRNA_det)
vennlists<- calculate.overlap(x = miRNA_det)
kit_union_names <- vennlists$a31

uniqueClontech<- seqs[which(names(seqs) %in% uniqueClontech),]
uniqueIllumina<- seqs[which(names(seqs) %in% uniqueIllumina),]
uniqueNEB<- seqs[which(names(seqs) %in% uniqueNEB),]
uniqueNEXTflex<- seqs[which(names(seqs) %in% uniqueNEXTflex),]
uniqueDeduped<- seqs[which(names(seqs) %in% uniqueDeduped),]
kit_union <- seqs[which(names(seqs) %in% kit_union_names),]
unique_seqs <-list(Clontech =uniqueClontech, Illumina =uniqueIllumina, NEB =uniqueNEB, NEXTFlex =uniqueNEXTflex)
#unique_seqs <-list(Clontech =uniqueClontech, NEB =uniqueNEB, NEXTFlex =uniqueNEXTflex)

length(uniqueClontech)
Biostrings::consensusString(uniqueClontech)
#length(uniqueIllumina)
length(uniqueNEB)
length(uniqueNEXTflex)
length(uniqueDeduped)

# t.test(width(uniqueNEB), width(uniqueClontech))
# t.test(width(uniqueNEB), width(uniqueNEXTflex))
# t.test(width(uniqueNEXTflex), width(uniqueClontech))
# t.test(width(kit_union), width(uniqueClontech))
# t.test(width(kit_union), width(uniqueNEB)) #maybe sig.. nit with bonferroni
# t.test(width(kit_union), width(uniqueNEXTflex))



GC_Clontech<-letterFrequency(uniqueClontech, letters = c("CG"), as.prob = TRUE)
GC_Illumina<-letterFrequency(uniqueIllumina, letters = c("CG"), as.prob = TRUE)
GC_NEB<-letterFrequency(uniqueNEB, letters = c("CG"), as.prob = TRUE)
GC_NEXTflex<-letterFrequency(uniqueNEXTflex, letters = c("CG"), as.prob = TRUE)
GC_Deduped<-letterFrequency(uniqueDeduped, letters = c("CG"), as.prob = TRUE)
GC_kitUnion<-letterFrequency(kit_union, letters = c("CG"), as.prob = TRUE)

GC_cont <- list(Clontech =GC_Clontech, Illumina =GC_Illumina, NEB =GC_NEB, NEXTflex = GC_NEXTflex, Deduped =GC_Deduped, Union =GC_kitUnion)

cols = gg_color_hue(n)
cols <-cols[1:6]
boxplot(GC_cont, col = cols, main = 'GC content of unique sequences across kits')

#bonferroni thresh = 0.0125
t.test(GC_kitUnion, GC_NEB)
#t.test(GC_kitUnion, GC_NEXTflex)
t.test(GC_kitUnion, GC_Illumina)## significant!!!!!!!!!!!!
t.test(GC_kitUnion, GC_Clontech)
t.test(GC_kitUnion, GC_Deduped) 

```





Ttests
```{r, echo = FALSE, message = FALSE, eval = TRUE}
library(dplyr)

  test_names <- data.frame(combn(names(GC_cont), m= 2))

get_test_results<- function(data,test_names) {
  tresults<<-list()
  tested_names1<<-list()
  tested_names2<<-list()
  for(i in names(test_names)){
    Kit1 <-data[which(names(data) %in% test_names[i][1,])]
    Kit2 <-data[which(names(data) %in% test_names[i][2,])]
    #Kit1<-data.frame(select(data, colnames(data)[colnames(data) %in% test_names[i][1,]]))
    #Kit2<-data.frame(select(data, colnames(data)[colnames(data) %in% test_names[i][2,]]))
    tested_names1[[i]]<<-names(data)[names(data) %in% test_names[i][1,]]
    tested_names2[[i]]<<-names(data)[names(data) %in% test_names[i][2,]]
    #colnames(Kit1)<-c("error")
    #colnames(Kit2)<-c("error")
    tresults[[i]]<<-t.test(x=Kit1[[1]], y=Kit2[[1]], paired = FALSE)
    tested_kits <<-paste0(tested_names1, "&", tested_names2)
  }
}

get_ttestStats<- function(x, tested_kits) {
  c(t =format(x$statistic, digits = 2),
    df = format(x$parameter, digits = 0),
    p.value = format(x$p.value, scientific = TRUE, digits = 2),
    bonferroni.thresh = format(.05/length(test_names), digits = 2),
    sig = ifelse(x$p.value<(.05/length(test_names)), "yes", "no"))
}
```




General GC content
```{r}
library(ggplot2)
get_seqs <- function(x){seqs[which(names(seqs) %in% x)]}
seqs_det<-lapply(miRNA_det, get_seqs)
names(seqs_det) <- names(split_kit_thresh)
seqs_det <- append(seqs_det, kit_union)
names(seqs_det)[6]<- c("Union")
names(seqs_det)[5]<- c("Deduped")

get_GC_content <- function(x) { letterFrequency(x, letters = c("CG"), as.prob = TRUE)}
GC_kits<-lapply(seqs_det, get_GC_content)



cols = gg_color_hue(n)
cols <-cols[1:6]
boxplot(GC_kits, col = cols, main = 'GC content of all miRNA detected across kits')


get_lengths<- function(x) { width(x)}
lengths_kits<-lapply(seqs_det, lengths)
lengths_unique<-lapply(unique_seqs, lengths)
lengths_unique<-append(lengths_unique, lengths_kits[6])
names(lengths_unique)[4]<- c("Union")

boxplot(lengths_kits, col = cols, main = 'Lengths of all miRNA detected across kits')
boxplot(lengths_unique, col = cols, main = 'Lengths of uniquely detected across kits')
#lapply(lengths_kits, make_hists)


library(reshape2)
lengths_melted<-melt(lengths_unique)
ggplot(lengths_melted, aes(x = value)) + geom_histogram() + facet_wrap(~ L1)
lengths_melted<-melt(lengths_kits)
ggplot(lengths_melted, aes(x = value)) + geom_histogram() + facet_wrap(~ L1)
ggplot(lengths_melted, aes(x = L1, y = value)) + geom_jitter() 

```
upset graph
```{r}
library(UpSetR)
library(plyr)
kit_union_names<-data.frame(union =kit_union_names)
miRNA <-append(miRNA_det, kit_union_names)
names(miRNA) <- names(seqs_det)
miRNA_df <-lapply(miRNA, data.frame)
miRNA_df_filled<- do.call(rbind.fill, miRNA_df)

```


```{r, eval =FALSE}
test_names <- data.frame(combn(names(lengths_unique), m= 2))
#test_names<-test_names[,which(test_names[1,] == "Union" | test_names[2,] == "Union")]

get_test_results(data = lengths_unique, test_names = test_names)
ttestStats_lengths_unique<-data.frame(lapply(tresults, get_ttestStats, tested_kits = tested_kits))
colnames(ttestStats_lengths_unique)<-tested_kits
ttestStats_lengths_unique
```

```{r}
test_names <- data.frame(combn(names(GC_cont), m= 2))
#test_names<-test_names[,which(test_names[1,] == "Union" | test_names[2,] == "Union")]


get_test_results(data = GC_kits, test_names = test_names)
ttestStats_GC_all<-data.frame(lapply(tresults, get_ttestStats, tested_kits = tested_kits))
colnames(ttestStats_GC_all)<-tested_kits
ttestStats_GC_all
```


#unique GC content
```{r}
test_names <- data.frame(combn(names(GC_cont), m= 2))
test_names<-test_names[,which(test_names[1,] == "Union" | test_names[2,] == "Union")]
#test_names<-test_names[,which(test_names[1,] != "Deduped" & test_names[2,] != "Deduped")]
#test_names<-test_names[,which(test_names[1,] != "Illumina" & test_names[2,] != "Illumina")]
test_names<-test_names[,which(test_names[1,] != "NEXTflex" & test_names[2,] != "NEXTflex")]
get_test_results(data = GC_cont, test_names = test_names)
ttestStats_GC_unique<-data.frame(lapply(tresults, get_ttestStats, tested_kits = tested_kits))
colnames(ttestStats_GC_unique)<-tested_kits
ttestStats_GC_unique
#thus the GC content is higher in Clontech compared to the union of all kits
```


distributions of detected reads
```{r}
get_widths <- function(x){plot(table(width(x)))}
lapply(seqs_det, get_widths)
unique_seqs<-unique_seqs[-grep("Illumina", names(unique_seqs))]
lapply(unique_seqs, get_widths)
```




logos- all detected
```{r}
#This is what we are using https://omarwagih.github.io/ggseqlogo/
#http://manuals.bioinformatics.ucr.edu/home/ht-seq#TOC-Position-Weight-Matrices-PWM-

library(seqLogo)
library(ggplot2)
library(ggseqlogo)

get22_seqs <- function(x) {x[which(width(x) == "22"),]}
det22_seqs <- lapply(seqs_det, get22_seqs)
Clontech_22<-data.frame(det22_seqs$Clontech)
Illumina_22<-data.frame(det22_seqs$Illumina)
NEB_22<-data.frame(det22_seqs$NEB)
NEXTflex_22<-data.frame(det22_seqs$NEXTflex)
Deduped_22<-data.frame(det22_seqs$Deduped)
Union_22<-data.frame(det22_seqs$Union)

the22_seqs <- list(Clontech_22, Illumina_22, NEB_22, NEXTflex_22, Deduped_22, Union_22)


#options for methods
#p1 = ggseqlogo( seqs_dna$MA0001.1, method = 'bits' )
#p2 = ggseqlogo( seqs_dna$MA0001.1, method = 'prob' )


p1 = ggseqlogo(Clontech_22$det22_seqs.Clontech, method = "bits")
p2 = ggseqlogo(Illumina_22$det22_seqs.Illumina, method = "bits")
p3 = ggseqlogo(NEB_22$det22_seqs.NEB, method = "bits")
p4 = ggseqlogo(NEXTflex_22$det22_seqs.NEXTflex, method = "bits")
p5 = ggseqlogo(Deduped_22$det22_seqs.Deduped, method = "bits")
p6 = ggseqlogo(Union_22$det22_seqs.Union, method = "bits")

gridExtra::grid.arrange(p1, p2, p3, p4)

gridExtra::grid.arrange(p1, p2, p3, p4, p5, p6)

#ggseqlogo(the22_seqs)
#ggseqlogo(seqs_dna, ncol=2)
#ggseqlogo(the22_seqs)


get_freq<- function(x){letterFrequency(x,  as.prob=TRUE, letters = c("A", "U", "C", "G"))}
freq_det_22seqs <-lapply(det22_seqs, get_freq)



```
logos- uniquely detected
```{r, eval = FALSE}
#This is what we are using https://omarwagih.github.io/ggseqlogo/
library(seqLogo)
library(ggplot2)
library(ggseqlogo)

unique22_seqs <- lapply(unique_seqs, get22_seqs)
Clontech_22_unique<-data.frame(unique22_seqs$Clontech)
#Illumina_22_unique<<-data.frame(unique22_seqs$Illumina)
NEXTflex_22_unique<<-data.frame(unique22_seqs$NEXTFlex)
NEB_22_unique<<-data.frame(unique22_seqs$NEB)

unique22seqs <- list(Clontech = Clontech_22_unique$unique22_seqs.Clontech,NEXTflex = NEXTflex_22_unique$unique22_seqs.NEXTFlex,NEB =NEB_22_unique$unique22_seqs.NEB, Union = Union_22$det22_seqs.Union)

ggseqlogo(unique22seqs, ncol=2, method="prob")
ggseqlogo(unique22seqs, ncol=2, method="bit")


  

lapply(unique22_seqs, length)

```


stat tests on seq
```{r, eval=FALSE, echo = FALSE}
library(limma)
library(plyr)
library(dplyr)
get_consensus <- function(x){ consensusMatrix(x, as.prob = TRUE, baseOnly = TRUE)}
unique22Matrices<-lapply(unique22_seqs, get_consensus)
kit22Matrices<-lapply(det22_seqs, get_consensus)

remove_other <- function(x){x[-(grep("other", rownames(x))),]}
kit22Matrices <- lapply(kit22Matrices, remove_other)

df <- t(ldply((kit22Matrices), data.frame))
colnames(df)<-df[1,]
df <- df[-1,]
base_names <- rep(c("A_", "C_", "G_", "U_"), 6)
kitpd <- data.frame(names(det22_seqs))
colnames(df)<-paste0(base_names, colnames(df))

A_by_loc<-data.frame(df[,grep("A_", colnames(df))])
C_by_loc<-data.frame(df[,grep("C_", colnames(df))])
G_by_loc<-data.frame(df[,grep("G_", colnames(df))])
U_by_loc<-data.frame(df[,grep("U_", colnames(df))])
convert <-function(x){as.numeric(as.character(x))}
A_by_loc<-data.frame(sapply(A_by_loc, convert))

seq_model<-lm(as.matrix(A_by_loc)~ kitpd$names.det22_seqs.)# not any replicates for a given location... so can't use this... wonder if there is a way to do some sort of chisquare at each location

#not sure how to deal with the fact that each base prob is extremely correlated to the other three base probablities. Not sure what to do here... I need a more raw dataframe of the counts for the sequences - could do a consensus for all the samples for a given kit... that doesn't seem quite right either...

design <- model.matrix(~kitpd$names.det22_seqs.)
f <- lmFit(A_by_loc, design)
f <- eBayes(f)


```


```{r, eval = FALSE}
library(seqinr)
test <-consensus(matrix(uniqueNEB), method = profile, type = "RNA")


word.list <- list(letters[1:4], letters[1:5], letters[1:2], letters[1:6])
n.obs <- sapply(word.list, length)
seq.max <- seq_len(max(n.obs))
mat <- t(sapply(word.list, "[", i = seq.max))
mt <-gsub("a", "A", mat)
mt <-gsub("b", "C", mt)
mt <-gsub("c", "C", mt)
mt <-gsub("d", "G", mt)
mt <-gsub("e", "U", mt)
mt <-gsub("f", "A", mt)
 (res <- consensus(phylip, method = "profile"))
> bxc <- barplot(res, col = c("green", "blue", "orange", "white", "red"), border = NA,
+   space = 0, las = 2, ylab = "Base count",
+   main = "Profile of a DNA sequence alignment",
+   xlab = "sequence position", xaxs = "i")
>   
>   text(x = bxc, y = par("usr")[4],lab = res.thr, pos = 3, xpd = NA)
>   text(x = bxc, y = par("usr")[1],lab = res.iup, pos = 1, xpd = NA)
```



I dont think this will work...dont have an error measurement...
```{r, include =TRUE, eval=FALSE}
#####Heatmap############
library(pheatmap)
library(Biostrings)


lastStuff<-function(str, n){result <-substr(str,(nchar(str)+1)-n,nchar(str))}
# 
kit_seqs<-as.data.frame(seqs_det$Clontech)
kit_seqs$name <-rownames(seqs)
rownames(kit_seqs) <- NULL



seqs_ordered<-as.character(kit_seqs$name[order(kit_seqs$x)], drop= FALSE)
seqs_orderedb<-as.character(kit_seqs$x[order(kit_seqs$x)], drop= FALSE)
#seqs_4_ordered <-strtrim(seqs_ordered, c(2))###uncomment to get first n bases and comment next line
seqs_4_ordered <-lastStuff(str=seqs_ordered, 3)####uncomment to get last n bases
error_ordered<-lapply(synth_error_pheat, function(x) x[order(kit_seqs$x)] )
error_ordered<-data.frame(error_ordered)
error_for_collapse<-data.frame(seq = seqs_4_ordered, error_ordered)
aggdata <-aggregate(error_ordered, by=list(seqs_4_ordered), FUN=mean)
errorM<-as.matrix(aggdata[,2:5])
rownames(errorM)<-aggdata[,1]
# 
# 
paletteLength <- 50
myColor <- colorRampPalette(c("yellow", "white", "blue"))(paletteLength)
myColor <- colorRampPalette(c("blue", "white", "red"))(paletteLength)
# 
myColor <- colorRampPalette(c("blue", "yellow", "red"))(paletteLength)
# 
#length(breaks) == length(paletteLength) + 1
# # use floor and ceiling to deal with even/odd length pallettelengths
#myBreaks <- c(seq(min(errorM), 0, length.out=ceiling(paletteLength/2) + 1), 
#               seq(max(errorM)/paletteLength, max(errorM), length.out=floor(paletteLength/2)))

#Plot the heatmap
#pheatmap(errorM, color=myColor, breaks=myBreaks)
# 
pheatmap(errorM, cluster_rows=F, cluster_cols=T, main = "First_3")#this does not allow for reordering of the rows.
pheatmap(errorM, main = "First_2")#this does not allow for reordering of the rows.
# 
# errorM_binary <- sign(errorM)
# pheatmap(errorM_binary, cluster_rows=F, cluster_cols=T, main = "First_3")
# 
# pheatmap(errorM, cluster_rows=F, cluster_cols=T, main = "First_3")

####HEATmap of length#######


# library(pheatmap)
# library(stringr)
# #below is a function to just have the last n bases of sequences with an example
# lastStuff<-function(str, n){result <-substr(str,(nchar(str)+1)-n,nchar(str))}
# 
 seqs<-as.data.frame(synth_seq)
 seqs<-as.character(seqs$x)
 lengths<-stringr::str_length(seqs)
 seqs_ordered <-seqs[order(lengths)]
 error_ordered<-lapply(synth_error_pheat, function(x) x[order(lengths)] )
 error_ordered<-data.frame(error_ordered)
 error_for_collapse<-data.frame(Length = lengths, error_ordered)
 aggdata <-aggregate(error_for_collapse, by=list(lengths), FUN=mean)
 errorM<-as.matrix(aggdata[,3:6])
 rownames(errorM)<-aggdata[,1]
# 
 pheatmap(errorM, cluster_rows=F, cluster_cols=T, main = "Length")#this does not allow for reordering of the rows.
```




```

