---
title: "Repro_1000_all_files_May7"
author: "Carrie Wright"
date: "5/7/2018"
output: html_document
---

```{r, eval=TRUE, echo=FALSE}
library(edgeR)
library(here)

Pheno<- read.table(here("18seed15limALLfiles/Pheno.csv"), header = T, sep = ",")
Pheno1000 <- Pheno[which(Pheno$startingAmt =="1000"),]#grab just the 1000ng samples

miR_counts<-read.table(here("18seed15limALLfiles/miR.Counts.csv"), header = TRUE, sep = ",")
rownames(miR_counts)<- miR_counts$miRNA#make miRNA rownames
miR_counts<-miR_counts[,2:length(colnames(miR_counts))]#remove miRNA col
miRNAtotal<-t(miR_counts[1,])#extract the total miRNA counts... in case we want them
miR_counts<-miR_counts[-1,]#remove total miRNA counts row
miR_counts<- miR_counts[which(Pheno$startingAmt=="1000")]#grab just the 1000ng samples

colnames(miR_counts)<-gsub("directional_dedupped|directional_deduped", "Deduped", colnames(miR_counts))
colnames(miR_counts)<-gsub("NEXT_", "NEXTflex_", colnames(miR_counts))

###To get rid of extra files
Pheno1000<-Pheno1000[-c(13:18),]
miR_counts<-miR_counts[-c(13:18)]



#Pheno1000$Kit<-gsub("NEXTflex_directional_deduped", "Deduped", Pheno1000$Kit)
# Pheno1000$Kit<-gsub("NEXTflex_Fivepercent", "Fivepercent", Pheno1000$Kit)
# Pheno1000$TriplicateGroup<-gsub("NEXTflex_directional_deduped", "Deduped", Pheno1000$TriplicateGroup)
# Pheno1000$TriplicateGroup<-gsub("NEXTflex_Fivepercent", "Fivepercent", Pheno1000$TriplicateGroup)
# colnames(miR_counts)<-gsub("directional_deduped_lib_align_seed15", "Deduped", colnames(miR_counts))
# colnames(miR_counts)<-gsub("NEXTflex_Fivepercent", "Fivepercent", colnames(miR_counts))

miR_1000_raw <-miR_counts
Pheno <-Pheno1000

#miR_1000_raw <- miR_1000_raw[-which(Pheno$Kit=="Fivepercent")]
#Pheno <- Pheno[-which(Pheno$Kit=="Fivepercent"),]

library(ggplot2)
# gg_color_hue <- function(n) {
#   hues = seq(15, 375, length = n + 1)
#   hcl(h = hues, l = 65, c = 100)[1:n]
# }
# n = 6
# cols = gg_color_hue(n)
# cols <-c(cols[1:4], cols[6], cols[5])


gg_color_hue <- function(n) {
  hues = seq(15, 375, length = n + 1)
  hcl(h = hues, l = 65, c = 100)[1:n]
}
n = 7
cols = gg_color_hue(n)
#cols <-c(cols[1:4], cols[6], cols[5])

#load("/Users/carriewright/Documents/miRNA seq Projects/miRNA_kit_comparison_project/DATA_ANALYSIS/UnionInfo.rda")
```

###DESeq2
```{r, eval=FALSE, warning=FALSE, message=FALSE, echo =FALSE}
library(DESeq2)
dds<-DESeqDataSetFromMatrix(countData = miR_1000_raw, colData = Pheno, design = ~ Kit)
dds <- estimateSizeFactors(dds)
norm_miR_1000<-data.frame(counts(dds, normalized = TRUE))
dim(norm_miR_1000)
```
###TMM Normalization

```{r, eval= TRUE, echo =FALSE}
library(edgeR)
group <-Pheno$Kit
d<-DGEList(counts = miR_1000_raw, group = group)
miR_1000_TMM_edgeR_factors <-calcNormFactors(d, method = "TMM")
TMM <-estimateCommonDisp(miR_1000_TMM_edgeR_factors)
norm_miR_1000 <-data.frame(TMM$pseudo.counts)
dim(norm_miR_1000)
```


```{r}
###split the data by kit
split_kit <- list() 
for(i in Pheno$Kit) { 
  split_kit[[i]] <- data.frame(norm_miR_1000[which(Pheno$Kit==i)])
} 

###split the data by kit and batch
split_batch <- list() 
for(i in Pheno$TriplicateGroup) { 
  split_batch[[i]] <- data.frame(norm_miR_1000[which(Pheno$TriplicateGroup==i)])
}
```

```{r}
###genefilter
library(genefilter)
poverafun <- genefilter::pOverA(p = 1, A = 10)#at least 100 normalized reads in all samples of the set... 

ffun <- filterfun(poverafun)
genefilt_fun<- function(x){genefilter(x, ffun)}
thresh<-lapply(split_kit, genefilt_fun)

split_kit_thresh <-list()
split_kit_thresh$Clontech<-split_kit$Clontech[thresh$Clontech,]
split_kit_thresh$Illumina<-split_kit$Illumina[thresh$Illumina,]
split_kit_thresh$NEB<-split_kit$NEB[thresh$NEB,]
split_kit_thresh$NEXTflex<-split_kit$NEXTflex[thresh$NEXTflex,]
split_kit_thresh$Double<-split_kit$Double[thresh$Double,]
split_kit_thresh$Deduped<-split_kit$Deduped[thresh$Deduped,]
split_kit_thresh$Fivepercent<-split_kit$Fivepercent[thresh$Fivepercent,]




thresh<-lapply(split_batch, genefilt_fun)


split_batch_thresh <-list()
split_batch_thresh$Clontech1000_Batch1<-split_batch$Clontech1000_Batch1[thresh$Clontech1000_Batch1,]
split_batch_thresh$Clontech1000_Batch2<-split_batch$Clontech1000_Batch2[thresh$Clontech1000_Batch2,]
split_batch_thresh$Illumina1000_Batch1<-split_batch$Illumina1000_Batch1[thresh$Illumina1000_Batch1,]
split_batch_thresh$Illumina1000_Batch2<-split_batch$Illumina1000_Batch2[thresh$Illumina1000_Batch2,]
split_batch_thresh$NEB1000_Batch1<-split_batch$NEB1000_Batch1[thresh$NEB1000_Batch1,]
split_batch_thresh$NEB1000_Batch2<-split_batch$NEB1000_Batch2[thresh$NEB1000_Batch2,]
split_batch_thresh$NEXTflex1000_Batch1<-split_batch$NEXTflex1000_Batch1[thresh$NEXTflex1000_Batch1,]
split_batch_thresh$NEXTflex1000_Batch2<-split_batch$NEXTflex1000_Batch2[thresh$NEXTflex1000_Batch2,]
split_batch_thresh$Double1000_Batch1 <-split_batch$Double1000_Batch1[thresh$Double1000_Batch1,]
split_batch_thresh$Double1000_Batch2<-split_batch$Double1000_Batch2[thresh$Double1000_Batch2,]
split_batch_thresh$Deduped1000_Batch1<-split_batch$Deduped1000_Batch1[thresh$Deduped1000_Batch1,]
split_batch_thresh$Deduped1000_Batch2<-split_batch$Deduped1000_Batch2[thresh$Deduped1000_Batch2,]
split_batch_thresh$Fivepercent1000_Batch1<-split_batch$Fivepercent1000_Batch1[thresh$Fivepercent1000_Batch1,]
split_batch_thresh$Fivepercent1000_Batch2<-split_batch$Fivepercent1000_Batch2[thresh$Fivepercent1000_Batch2,]



split_batch_thresh_batch1 <- split_batch_thresh[grep("Batch1", names(split_batch_thresh))]
split_batch_thresh_batch2 <- split_batch_thresh[grep("Batch2", names(split_batch_thresh))]
```


```{r}
###The Function
library(limma)
library(edgeR)

single <- function(kit) {
  dat<-split_kit_thresh[grep(kit, names(split_kit_thresh))]
  dat<-data.frame(dat)
  p <- Pheno[grep(kit, (Pheno[, 2])), ]
  design <- model.matrix(~p$Batch)
  data_s <<- log2(dat + 1)
  f <- lmFit(data_s, design)
  f <- eBayes(f)
}
```

```{r}
kits<-as.character(unique(Pheno$Kit))
fits <-lapply(kits, single)
names(fits) <-kits
```

Try one kit manually
```{r}
Clontech_raw <-log2(split_kit_thresh$Clontech +1)
NEB_raw <-log2(split_kit_thresh$NEB +1)
Fivepercent_raw <-log2(split_kit_thresh$Fivepercent +1)
Deduped_raw<-log2(split_kit_thresh$Deduped +1)
p <- Pheno[grep("Clontech", Pheno$Kit),]

lm_clontec_1 <- lm(t(Clontech_raw) ~ p$Batch)#same first coeffecient as bellow but slightly different output - this allows with summary to get the indivudal p values without ebayes... but I am not sure how to easily grab them all 
summary(lm_clontec_1)
lm_NEB_1 <- lm(t(NEB_raw) ~ p$Batch)
lm_Deduped_1 <- lm(t(Deduped_raw) ~ p$Batch)
lm_Fivepercent_1 <- lm(t(Fivepercent_raw) ~ p$Batch)
summary(fit)$r.squared #this will pull out the r squred values - the percent of variance explained by the predictor variable
#in this case we would need :
summary(lm_clontec_1)$"Response hsa-miR-99b-5p"$r.squared
summary(lm_clontec_1)$"Response hsa-miR-99b-5p"$coefficients[,4]
summary(lm_clontec_1)$"Response hsa-miR-99b-5p"$coefficients[,4][[2]]
#summary(fit)$coefficients[,4]  #this will pull out the p values normally
Clontechpvalues <- lapply(summary(lm_clontec_1), function(f){f$coefficients[,4][[2]]})
Clontech_p<--log(data.frame(unlist(Clontechpvalues)))
NEBpvalues <- lapply(summary(lm_NEB_1), function(f){f$coefficients[,4][[2]]})
NEB_p<--log(data.frame(unlist(NEBpvalues)))
Dedupedpvalues <- lapply(summary(lm_Deduped_1), function(f){f$coefficients[,4][[2]]})
Fivepercentpvalues <- lapply(summary(lm_Fivepercent_1), function(f){f$coefficients[,4][[2]]})
Deduped_p<--log(data.frame(unlist(Dedupedpvalues)))

Fivepercent_p<--log(data.frame(unlist(Fivepercentpvalues)))
lm_pvalues <-list(NEB_p, Clontech_p, Deduped_p, Fivepercent_p)

t.test(NEB_p, Clontech_p)
library(reshape2)
pvals<-melt(lm_pvalues)
ggplot(data =pvals, aes (x = pvals$variable, y = pvals$value, color = pvals$variable))+geom_boxplot()


design <- model.matrix(~p$Batch)
lm_clontech <- lmFit(Clontech_raw, design)
ebayes_clontech <- eBayes(lm_clontech)
head(ebayes_clontech$p.value)
t.test(Clontech_raw[1,][1:3], Clontech_raw[1,][4:6])
head(lm_clontech$coefficients)
```



Evaluate Batch P values
```{R, eval = TRUE}
##########pvalues etc.#####
pval_single <-list()
pval_single<-lapply(fits, function(f) { f$p.value[, 2] })
pval_df_single <-lapply(pval_single, data.frame)
qval_single <- sapply(pval_single, p.adjust, method = 'fdr')
qval_df_single <-lapply(qval_single, data.frame)
tval_single<-lapply(fits, function(f) { f$t[, 2] })
tval_df_single <-lapply(tval_single, data.frame)


raw_table<-sapply(qval_df_single, function(x) { table(x > 0.05 )}) # TRUE = not sig accross batch is true
raw_table
percent_table_noBatcheffect<-(raw_table[which(rownames(raw_table) == "TRUE"),] / colSums(raw_table))*100
percent_table_Batcheffect<-(raw_table[which(rownames(raw_table) == "FALSE"),] / colSums(raw_table))*100
#round(sapply(qval_df_single, function(x) { table(x > 0.05 )}) / nrow(qval_df_single) * 100, 2)

```




###Paired Test
```{r, echo = FALSE, message = FALSE, eval = TRUE}
library(dplyr)

#Names_thresh<-(intersect(intersect(intersect(intersect(rownames(split_kit_thresh[[1]]), rownames(split_kit_thresh[[2]])), rownames(split_kit_thresh[[3]])), rownames(split_kit_thresh[[4]])), rownames(split_kit_thresh[[5]])))

#Names_thresh<-intersect(intersect(intersect(intersect(intersect(rownames(split_kit_thresh[[1]]), rownames(split_kit_thresh[[2]])), rownames(split_kit_thresh[[3]])), rownames(split_kit_thresh[[4]])), rownames(split_kit_thresh[[5]])), rownames(split_kit_thresh[[6]]))

Names_thresh<-intersect(intersect(intersect(intersect(intersect(intersect(rownames(split_kit_thresh[[1]]), rownames(split_kit_thresh[[2]])), rownames(split_kit_thresh[[3]])), rownames(split_kit_thresh[[4]])), rownames(split_kit_thresh[[5]])), rownames(split_kit_thresh[[6]])), rownames(split_kit_thresh[[7]]))

finding_rows<-function(x){x[rownames(x) %in% Names_thresh,]}



pvalues <- sapply(pval_df_single, finding_rows)
rownames(pvalues)<- Names_thresh
qvalues <- sapply(data.frame(pvalues), p.adjust, method = 'fdr')#this is limited to just those in the intersection... so the q adjustment is slightly diff than bellow
boxplot(-log(pvalues))
boxplot(-log(qvalues))
tvalues <-sapply(tval_df_single, finding_rows)

qvals <- lapply(qval_df_single, finding_rows)  
qvals <- data.frame(qvals)
colnames(qvals)<-names(qval_df_single)
#qvals <- -log10(qvals)
  test_names <- data.frame(combn(kits, m= 2))

get_test_results<- function(data,test_names, pairedvalue) {
  tresults<<-list()
  tested_names1<<-list()
  tested_names2<<-list()
  for(i in names(test_names)){
    Kit1 <-data[which(names(data) %in% test_names[i][1,])]
    Kit2 <-data[which(names(data) %in% test_names[i][2,])]
    Kit1<-data.frame(select(data, colnames(data)[colnames(data) %in% test_names[i][1,]]))
    Kit2<-data.frame(select(data, colnames(data)[colnames(data) %in% test_names[i][2,]]))
    tested_names1[[i]]<<-names(data)[names(data) %in% test_names[i][1,]]
    tested_names2[[i]]<<-names(data)[names(data) %in% test_names[i][2,]]
    colnames(Kit1)<-c("error")
    colnames(Kit2)<-c("error")
    tresults[[i]]<<-t.test(x=Kit1[[1]], y=Kit2[[1]], paired = pairedvalue)
    tested_kits <<-paste0(tested_names1, "&", tested_names2)
  }
}

get_ttestStats<- function(x, tested_kits) {
  c(t =format(x$statistic, digits = 2),
    df = format(x$parameter, digits = 0),
    p.value = format(x$p.value, scientific = TRUE, digits = 2),
    bonferroni.threshold = format(.05/length(test_names), digits = 2),
    sig = ifelse(x$p.value<(.05/length(test_names)), "yes", "no"))
}
```


```{r}
Qs <-qvals
Qs$miRNA <-Names_thresh
Qs <-melt(Qs)
Qs_only <-Qs[which(Qs$variable =="Fivepercent"),]

#Qs$variable <- factor(Qs$variable, levels =c("Clontech","Illumina","NEB","NEXTflex","Double", "Deduped","Fivepercent"))
 plot1001<-ggplot(data = Qs, aes(x = miRNA, y = value, color= variable))+geom_jitter(alpha =0.7)+
      ggtitle(label = "Batch sig value across kits")+ 
      labs(y =  "batch effect \n on indv. miRNAs")+
      theme(axis.title.x = element_text(size =0), 
            plot.title = element_text(size = 30, face = "bold", hjust = 0.5), 
            axis.text.x = element_text(size = 10),
            axis.text.y = element_text(size = 20), 
            axis.title.y = element_text(size =15),
            legend.position= "none") 
    plot1001
   
     plot1001<-ggplot(data = Qs_only, aes(x = miRNA, y = value))+geom_point(alpha =0.7)+
      ggtitle(label = "Batch sig value across kits")+ 
      labs(y =  "batch effect \n on indv. miRNAs")+
      theme(axis.title.x = element_text(size =0), 
            plot.title = element_text(size = 30, face = "bold", hjust = 0.5), 
            axis.text.x = element_text(size = 10),
            axis.text.y = element_text(size = 20), 
            axis.title.y = element_text(size =15),
            legend.position= "none") 
    plot1001
    
    
    Qs_only <-Qs[which(Qs$variable =="Deduped"),]
    
    plot1001<-ggplot(data = Qs_only, aes(x = miRNA, y = value))+geom_point(alpha =0.7)+
      ggtitle(label = "Batch sig value across kits")+ 
      labs(y =  "batch effect \n on indv. miRNAs")+
      theme(axis.title.x = element_text(size =0), 
            plot.title = element_text(size = 30, face = "bold", hjust = 0.5), 
            axis.text.x = element_text(size = 10),
            axis.text.y = element_text(size = 20), 
            axis.title.y = element_text(size =15),
            legend.position= "none") 
    plot1001
    
    
    expression <- lapply(split_kit_thresh, finding_rows) 
    
  test<-lapply(expression, log2)
    
    Deduped_batch2 <- rowMeans(test$Deduped[1:3])
    Deduped_batch1 <- rowMeans(test$Deduped[4:6])
    Deduped <- data.frame(cbind(Deduped_batch1, Deduped_batch2))
    Deduped$miRNA <- rownames(Deduped)
    Deduped_100 <- Deduped[1:100,]
    Deduped <- melt(Deduped_100)

   
     plot1001<-ggplot(data = Deduped, aes(x = miRNA, y = value, color= variable))+geom_point(alpha =0.7)+
      ggtitle(label = "Deduped")+ 
      labs(y =  "Expression of indv. miRNAs")+
      theme(axis.title.x = element_text(size =0), 
            plot.title = element_text(size = 30, face = "bold", hjust = 0.5), 
            axis.text.x = element_text(size = 3, angle = 90),
            axis.text.y = element_text(size = 20), 
            axis.title.y = element_text(size =15),
            legend.position= "none") 
    plot1001
    
    Fivepercent_batch2 <- rowMeans(test$Fivepercent[1:3])
    Fivepercent_batch1 <- rowMeans(test$Fivepercent[4:6])
    Fivepercent <- data.frame(cbind(Fivepercent_batch1, Fivepercent_batch2))
    Fivepercent$miRNA <- rownames(Fivepercent)
    Fivepercent_100 <- Fivepercent[1:100,]
    Fivepercent <- melt(Fivepercent_100)

   
     plot1002<-ggplot(data = Fivepercent, aes(x = miRNA, y = value, color= variable))+geom_point(alpha =0.7)+
      ggtitle(label = "Fivepercent")+ 
      labs(y =  "Expression of indv. miRNAs")+
      theme(axis.title.x = element_text(size =0), 
            plot.title = element_text(size = 30, face = "bold", hjust = 0.5), 
            axis.text.x = element_text(size = 3, angle = 90),
            axis.text.y = element_text(size = 20), 
            axis.title.y = element_text(size =15),
            legend.position= "none") 
    plot1002
    
    
    NEB_batch2 <- rowMeans(test$NEB[1:3])
    NEB_batch1 <- rowMeans(test$NEB[4:6])
    NEB <- data.frame(cbind(NEB_batch1, NEB_batch2))
    NEB$miRNA <- rownames(NEB)
    NEB_100 <- NEB[1:100,]
    NEB <- melt(NEB_100)

   
     plot1003<-ggplot(data = NEB, aes(x = miRNA, y = value, color= variable))+geom_point(alpha =0.7)+
      ggtitle(label = "NEB")+ 
      labs(y =  "Expression of indv. miRNAs")+
      theme(axis.title.x = element_text(size =0), 
            plot.title = element_text(size = 30, face = "bold", hjust = 0.5), 
            axis.text.x = element_text(size = 3, angle = 90),
            axis.text.y = element_text(size = 20), 
            axis.title.y = element_text(size =15),
            legend.position= "none") 
    plot1003
    library(gridExtra)
    grid.arrange(plot1001, plot1002, plot1003, ncol = 1)
    
    
    
    #### plot the difference between the means of the batches
    Deduped_batch2 <- rowMeans(test$Deduped[1:3])
    Deduped_batch1 <- rowMeans(test$Deduped[4:6])
    Deduped <- data.frame(difference =abs(Deduped_batch1- Deduped_batch2))
    Deduped$miRNA <- rownames(Deduped)
    Deduped_100 <- Deduped
    Deduped <- melt(Deduped_100)

   
     plot1001<-ggplot(data = Deduped, aes(x = miRNA, y = value))+geom_col(alpha =0.7)+
      ggtitle(label = "Deduped")+ 
      labs(y =  "Expression of indv. miRNAs")+
      theme(axis.title.x = element_text(size =0), 
            plot.title = element_text(size = 30, face = "bold", hjust = 0.5), 
            axis.text.x = element_text(size = 3, angle = 90),
            axis.text.y = element_text(size = 20), 
            axis.title.y = element_text(size =15),
            legend.position= "none") + ylim(0,1)
    plot1001
    
    Fivepercent_batch2 <- rowMeans(test$Fivepercent[1:3])
    Fivepercent_batch1 <- rowMeans(test$Fivepercent[4:6])
    Fivepercent <- data.frame(difference =abs(Fivepercent_batch1- Fivepercent_batch2))
    Fivepercent$miRNA <- rownames(Fivepercent)
    Fivepercent_100 <- Fivepercent
    Fivepercent <- melt(Fivepercent_100)

   
     plot1002<-ggplot(data = Fivepercent, aes(x = miRNA, y = value))+geom_col(alpha =0.7)+
      ggtitle(label = "Fivepercent")+ 
      labs(y =  "Expression of indv. miRNAs")+
      theme(axis.title.x = element_text(size =0), 
            plot.title = element_text(size = 30, face = "bold", hjust = 0.5), 
            axis.text.x = element_text(size = 3, angle = 90),
            axis.text.y = element_text(size = 20), 
            axis.title.y = element_text(size =15),
            legend.position= "none") + ylim(0,1)
    plot1002 
    
    
    NEB_batch2 <- rowMeans(test$NEB[1:3])
    NEB_batch1 <- rowMeans(test$NEB[4:6])
    NEB <- data.frame(difference =abs((NEB_batch1- NEB_batch2)))
    NEB$miRNA <- rownames(NEB)
    NEB_100 <- NEB
    NEB <- melt(NEB_100)

   
       plot1003<-ggplot(data = NEB, aes(x = miRNA, y = value))+geom_col(alpha =0.7)+
      ggtitle(label = "NEB")+ 
      labs(y =  "Expression of indv. miRNAs")+
      theme(axis.title.x = element_text(size =0), 
            plot.title = element_text(size = 30, face = "bold", hjust = 0.5), 
            axis.text.x = element_text(size = 3, angle = 90),
            axis.text.y = element_text(size = 20), 
            axis.title.y = element_text(size =15),
            legend.position= "none") + ylim(0,1)
    plot1003
  
    
    Clontech_batch2 <- rowMeans(test$Clontech[1:3])
    Clontech_batch1 <- rowMeans(test$Clontech[4:6])
    Clontech <- data.frame(difference =abs((Clontech_batch1- Clontech_batch2)))
    Clontech$miRNA <- rownames(Clontech)
    Clontech_100 <- Clontech
   Clontech <- melt(Clontech_100)

   
       plot1004<-ggplot(data = Clontech, aes(x = miRNA, y = value))+geom_col(alpha =0.7)+
      ggtitle(label = "Contech")+ 
      labs(y =  "Expression of indv. miRNAs")+
      theme(axis.title.x = element_text(size =0), 
            plot.title = element_text(size = 30, face = "bold", hjust = 0.5), 
            axis.text.x = element_text(size = 3, angle = 90),
            axis.text.y = element_text(size = 20), 
            axis.title.y = element_text(size =15),
            legend.position= "none") + ylim(0,1)
    plot1004
    library(gridExtra)
    grid.arrange(plot1001, plot1002, plot1003, plot1004, ncol = 1)
    
     Illumina_batch2 <- rowMeans(test$Illumina[1:3])
    Illumina_batch1 <- rowMeans(test$Illumina[4:6])
    Illumina <- data.frame(difference =abs((Illumina_batch1- Illumina_batch2)))
    Illumina$miRNA <- rownames(Illumina)
    Illumina_100 <- Illumina
   Illumina <- melt(Illumina_100)
   
    NEXTflex_batch2 <- rowMeans(test$NEXTflex[1:3])
    NEXTflex_batch1 <- rowMeans(test$NEXTflex[4:6])
    NEXTflex <- data.frame(difference =abs((NEXTflex_batch1- NEXTflex_batch2)))
    NEXTflex$miRNA <- rownames(NEXTflex)
    NEXTflex_100 <- NEXTflex
   NEXTflex <- melt(NEXTflex_100)
   
    Double_batch2 <- rowMeans(test$Double[1:3])
    Double_batch1 <- rowMeans(test$Double[4:6])
    Double <- data.frame(difference =abs((Double_batch1- Double_batch2)))
    Double$miRNA <- rownames(Double)
    Double_100 <- Double
   Double <- melt(Double_100)
    ###########Boxplots
    
    differences <- data.frame( Clontech$value, Illumina$value, NEB$value, NEXTflex$value, Double$value, Deduped$value, Fivepercent$value)
   colnames(differences)<- c("Clontech", "Illumina", "NEB", "NEXTflex", "Double", "Deduped","Fivepercent")
        boxplot(differences)
        diff <-melt(differences)
        ggplot(data = diff, aes(x=variable, y = value))+geom_jitter()+geom_boxplot()
        
        #in this case we want the t to be low (t = differences between batch)
        
```
Standard Deviation
```{r}
#test is just the intersection
#split_kit_thresh is all rows
sdtest <- lapply(test,rowSds)#genefilter
boxplot(sdtest)

test_names <- data.frame(combn(kits, m= 2))

get_test_results<- function(data,test_names, pairedvalue) {
  tresults<<-list()
  tested_names1<<-list()
  tested_names2<<-list()
  for(i in names(test_names)){
    Kit1 <-data[which(names(data) %in% test_names[i][1,])]
    Kit2 <-data[which(names(data) %in% test_names[i][2,])]
    Kit1<-data.frame(select(data, colnames(data)[colnames(data) %in% test_names[i][1,]]))
    Kit2<-data.frame(select(data, colnames(data)[colnames(data) %in% test_names[i][2,]]))
    tested_names1[[i]]<<-names(data)[names(data) %in% test_names[i][1,]]
    tested_names2[[i]]<<-names(data)[names(data) %in% test_names[i][2,]]
    colnames(Kit1)<-c("error")
    colnames(Kit2)<-c("error")
    tresults[[i]]<<-t.test(x=Kit1[[1]], y=Kit2[[1]], paired = pairedvalue)
    tested_kits <<-paste0(tested_names1, "&", tested_names2)
  }
}

get_ttestStats<- function(x, tested_kits) {
  c(t =format(x$statistic, digits = 2),
    df = format(x$parameter, digits = 0),
    p.value = format(x$p.value, scientific = TRUE, digits = 2),
    bonferroni.threshold = format(.05/length(test_names), digits = 2),
    sig = ifelse(x$p.value<(.05/length(test_names)), "yes", "no"))
}

#higher t is worse because we are using sds
get_test_results(data = data.frame(sdtest), test_names = test_names, pairedvalue = TRUE)
ttestStats_across<-data.frame(lapply(tresults, get_ttestStats, tested_kits = tested_kits))
colnames(ttestStats_across)<-tested_kits
ttestStats_across

sdtest <-data.frame(sdtest)

get_test_results(data = differences, test_names = test_names, pairedvalue = TRUE)
ttestStats_across<-data.frame(lapply(tresults, get_ttestStats, tested_kits = tested_kits))
colnames(ttestStats_across)<-tested_kits
ttestStats_across



get_test_results(data = data.frame(qvalues), test_names = test_names, pairedvalue = TRUE)
ttestStats_across<-data.frame(lapply(tresults, get_ttestStats, tested_kits = tested_kits))
colnames(ttestStats_across)<-tested_kits
ttestStats_across


get_test_results(data = data.frame(abs(tvalues)), test_names = test_names, pairedvalue = TRUE)
ttestStats_across<-data.frame(lapply(tresults, get_ttestStats, tested_kits = tested_kits))
colnames(ttestStats_across)<-tested_kits
ttestStats_across

#summary(lm(sdtest~colnames(sdtest)))
```


in this case... a lower t is worse... because we are using the qvals for batch effect significance
```{r, eval = TRUE}
#get_test_names(qval_df_single, eval = FALSE)
get_test_results(data = qvals, test_names = test_names, pairedvalue = TRUE)
ttestStats_across<-data.frame(lapply(tresults, get_ttestStats, tested_kits = tested_kits))
colnames(ttestStats_across)<-tested_kits
ttestStats_across
```

Accross Batch Error Plot
```{r, eval=TRUE}
library(ggplot2)
library(reshape2)



qvals <- -log10(qvals)



make_plot <- function(qvals, coef = FALSE) {
qvals$variable <- factor(qvals$variable, levels =c("Clontech","Illumina","NEB","NEXTflex","Double", "Deduped","Fivepercent"))
    plot1001<-ggplot(data = qvals, aes(x = variable, y = value, color= variable))+geom_jitter(alpha =0.7) +geom_jitter(outlier.shape = NA, varwidth = TRUE)+
      ggtitle(label = "Inconsistency Across Batch")+ 
      labs(y = ifelse(coef, "Coef for batch effect \n on indv. miRNAs", "-log10(q) for batch effect \n on indv. miRNAs"))+
      theme(axis.title.x = element_text(size =0), 
            plot.title = element_text(size = 30, face = "bold", hjust = 0.5), 
            axis.text.x = element_text(size = 10),
            axis.text.y = element_text(size = 20), 
            axis.title.y = element_text(size =15),
            legend.position= "none") 
    plot1001
    
    
    
    #+scale_fill_manual(values=kit_colors)+ scale_color_manual(values=rep("black", 5)) #+geom_jitter(aes(fill = variable, alpha =.3))+scale_fill_manual(values=kit_colors)+ scale_color_manual(values=rep("black", 5))
    
    plot1001  +scale_fill_manual(values=cols)+ scale_color_manual(values=rep("black", 6)) + geom_point() + scale_color_manual(values=cols) + geom_boxplot(alpha =0.7)
    plot1001  +scale_fill_manual(values=cols)+ scale_color_manual(values=rep("black", 6)) + geom_point(outlier.shape = NA) + scale_color_manual(values=cols)+ geom_boxplot(alpha =0.7,outlier.shape = NA)
}

make_plot(qvals =melt((qvals)))



```


###Evaluate Within Batch Error Function#
```{r, echo=TRUE, message=FALSE, warning=FALSE, eval = TRUE}

library(reshape2)
library(limma)
library(edgeR)
library(dplyr)


test_names <- data.frame(combn(Pheno$TriplicateGroup, m= 2))
  
get_error<- function(data) {
  errorData <<-list()
  errordata <<-data.frame()
  #error_for_graph <<-list()
  for(i in names(data)){
  data_kit <<-data.frame(data[grep(i,names(data))])
  errordata <-data_kit - rowMeans(data_kit)
  errordata <-abs(errordata)
  #error_for_graph<<-melt(errordata)
  errordata <-log2(errordata +1)
  errorData[[i]]<<-errordata
  }
}

```

Higher t is worse = higher error

###Within Error Batch 1 
```{r}
get_error(data = split_batch_thresh_batch1)

mean_errors_1 <- lapply(errorData, rowMeans)


test_names <- data.frame(combn(names(split_batch_thresh_batch1), m= 2))

errorData_test <-lapply(mean_errors_1, data.frame)
errorData_test <- lapply(errorData_test, finding_rows)  
errorData_test <- data.frame(errorData_test)
colnames(errorData_test) <-names(split_batch_thresh_batch1)



get_test_results(data = errorData_test, test_names = test_names, pairedvalue = TRUE)
#get_test_results(data = mean_errors_1, test_names = test_names)

ttestStats_within_1<-data.frame(lapply(tresults, get_ttestStats, tested_kits = tested_kits))
colnames(ttestStats_within_1)<-tested_kits
ttestStats_within_1

###FIX!!!!!!!!!!
log_batch1 <- lapply(split_batch_thresh_batch1, log2)
sdbatch1 <- lapply(log_batch1,rowSds)
sdbatch1 <-lapply(sdbatch1, data.frame)
sdbatch1_int <- lapply(sdbatch1, finding_rows)

meltedsd <-melt(sdbatch1_int)
meltedsd$L1 <- factor(meltedsd$L1, levels =c("Clontech1000_Batch1","Illumina1000_Batch1","NEB1000_Batch1","NEXTflex1000_Batch1","Double1000_Batch1", "Deduped1000_Batch1","Fivepercent1000_Batch1"))
ggplot(data = meltedsd, aes(x = L1, y = value)) + geom_boxplot()

log_batch2 <- lapply(split_batch_thresh_batch2, log2)
sdbatch2 <- lapply(log_batch2,rowSds)
sdbatch2 <-lapply(sdbatch2, data.frame)
sdbatch2_int <- lapply(sdbatch2, finding_rows)

meltedsd <-melt(sdbatch2_int)
meltedsd$L1 <- factor(meltedsd$L1, levels =c("Clontech1000_Batch2","Illumina1000_Batch2","NEB1000_Batch2","NEXTflex1000_Batch2","Double1000_Batch2", "Deduped1000_Batch2","Fivepercent1000_Batch2"))
ggplot(data = meltedsd, aes(x = L1, y = value)) + geom_boxplot()


get_test_results(data = sdbatch1, test_names = test_names, pairedvalue = FALSE)
ttestStats_within_1<-data.frame(lapply(tresults, get_ttestStats, tested_kits = tested_kits))
colnames(ttestStats_within_1)<-tested_kits
ttestStats_within_1

get_test_results(data = sdbatch1_int, test_names = test_names, pairedvalue = TRUE)
ttestStats_within_1<-data.frame(lapply(tresults, get_ttestStats, tested_kits = tested_kits))
colnames(ttestStats_within_1)<-tested_kits
ttestStats_within_1

```

###Within Error Plots Batch 1###########
```{r, echo=FALSE, warning=FALSE, eval=TRUE}
library(ggplot2)

melted_errordata_1 <- melt(errorData_test)
Within_error_df <- melted_errordata_1
Within_error_df$variable<-gsub("1000_Batch1", "", Within_error_df$variable)

make_plot <- function(Within_error_df) {
    Within_error_df$variable <- factor(Within_error_df$variable, levels =c("Clontech","Illumina","NEB","NEXTflex","Double", "Deduped","Fivepercent"))
    #Within_error_df$variable <- factor(Within_error_df$variable, levels =c("Clontech","Illumina","NEB","NEXTflex","Deduped"))
  plot1000<<-ggplot(data = melt(Within_error_df), aes(x = variable, y = value, color= variable)) +geom_jitter(aes(color = variable, alpha =.7)) +
  theme(axis.title.x = element_text(size =0), 
        plot.title = element_text(size = 18, face = "bold", hjust = 0.1), 
        axis.text.x = element_text(size = 10),
        axis.text.y = element_text(size = 10), 
        axis.title.y = element_text(size =18))
}
make_plot(Within_error_df = Within_error_df)

# if you want the original plot colors :
#plot1000 +scale_color_manual(values=kit_colors) + theme(legend.position = "none") + labs(y = "Absolute error from the mean", title = "Within batch error across kits in first batch") + ylim(0,10000)

# if you want boxplot : +geom_boxplot(aes(fill = L1, alpha =.7), outlier.shape = NA)

plot1000  + theme(legend.position = "none") + labs(y = "Absolute error from the mean", title = "Within batch error across kits in first batch") + geom_boxplot(varwidth = TRUE, outlier.shape = NA)
```
###Within Error Batch 2
```{r}
get_error(data = split_batch_thresh_batch2)

mean_errors_2 <- lapply(errorData, rowMeans)
melted_errordata_2 <- melt(errorData)


test_names <- data.frame(combn(names(split_batch_thresh_batch2), m= 2))

errorData_test <-lapply(mean_errors_2, data.frame)
errorData_test <- lapply(errorData_test, finding_rows)  
errorData_test <- data.frame(errorData_test)
colnames(errorData_test) <-names(split_batch_thresh_batch2)

get_test_results(data = errorData_test, test_names = test_names, pairedvalue = TRUE)
#get_test_results(data = mean_errors_2, test_names = test_names)

ttestStats_within_2<-data.frame(lapply(tresults, get_ttestStats, tested_kits = tested_kits))
colnames(ttestStats_within_2)<-tested_kits
ttestStats_within_2


```

###Within Error Plots Batch 2###########
```{r, echo=FALSE, warning=FALSE, eval=TRUE}
library(ggplot2)


melted_errordata_2 <- melt(errorData_test)
Within_error_df <- melted_errordata_2
Within_error_df$variable<-gsub("1000_Batch2", "", Within_error_df$variable)

# make_plot(Within_error_df = Within_error_df)
# plot1000 +scale_fill_manual(values=kit_colors) + theme(legend.position = "none") + labs(y = "Absolute error from the mean", title = "Within batch error across kits in second batch") + ylim(0,10000)

make_plot(Within_error_df = Within_error_df)
plot1000 + theme(legend.position = "none") + labs(y = "Absolute error from the mean", title = "Within batch error across kits in second batch") + geom_boxplot(varwidth = TRUE, outlier.shape = NA)
```
```{r}
ttestStats_within_1
#this time larger t is worse performance - larger error
```

```{r}
ttestStats_within_2
#this time larger t is worse performance - larger error
```




######################
##Mean within error of both batches

```{r, eval = TRUE}

  mean_errors_avg <- list()

get_means <-function(kits) {
  for(i in kits){
  intersection <- rownames(as.data.frame(mean_errors_1[grep(i,  names(mean_errors_1))]))[which(rownames(as.data.frame(mean_errors_1[grep(i, names(mean_errors_1))])) %in% rownames(as.data.frame(mean_errors_2[grep(i, names(mean_errors_2))])))]
   batch1<-as.data.frame(mean_errors_1[grep(i, names(mean_errors_1))])[which(rownames(as.data.frame(mean_errors_1[grep(i, names(mean_errors_1))])) %in% intersection), , drop = FALSE]
   batch2<-as.data.frame(mean_errors_2[grep(i,     names(mean_errors_2))])[which(rownames(as.data.frame(mean_errors_2[grep(i, names(mean_errors_2))])) %in% intersection), , drop = FALSE]
  kit_together<-cbind(batch1, batch2)
  mean_errors_avg[[i]]<<-rowMeans(kit_together)
  }
}


kits <-names(split_kit)
results<-lapply(kits, get_means) 


test_names <- data.frame(combn(names(split_kit), m= 2))

errorData_test <-lapply(mean_errors_avg, data.frame)
errorData_test <- lapply(errorData_test, finding_rows)  
errorData_test <- data.frame(errorData_test)
colnames(errorData_test) <-names(split_kit_thresh)

get_test_results(data = errorData_test, test_names = test_names, pairedvalue = TRUE)

ttestStats_within_avg<-data.frame(lapply(tresults, get_ttestStats, tested_kits = tested_kits))
colnames(ttestStats_within_avg)<-tested_kits

ttestStats_within_avg

```
##mean within error plot
```{r, echo=FALSE, warning=FALSE, eval=TRUE, message=FALSE}
library(ggplot2)

melted_errordata_avg <- melt(errorData_test)
Within_error_df <- melted_errordata_avg
  
make_plot(Within_error_df = Within_error_df)
plot1000  + theme(legend.position = "none") + labs(y = "Absolute error from the mean", title = "Average within batch error across kits")

#plot1000  + theme(legend.position = "none") + labs(y = "Absolute error from the mean", title = "Average within batch error across kits")  + geom_boxplot(varwidth = TRUE, outlier.shape = NA)
```

Standard deviation
```{r}

#Looking at batch...
split_kit_thresh$Fivepercent[1,]
t.test(split_kit_thresh$Fivepercent[1,][1:3],split_kit_thresh$Fivepercent[1,][4:6])
split_kit_thresh$NEXTflex[1,]
t.test(split_kit_thresh$NEXTflex[1,][1:3],split_kit_thresh$NEXTflex[1,][4:6])

head(fits$Fivepercent$p.value)
t.test(split_kit_thresh$Fivepercent[1,][1:3],split_kit_thresh$Fivepercent[1,][4:6])

head(fits$NEXTflex$p.value)
t.test(split_kit_thresh$NEXTflex[1,][1:3],split_kit_thresh$NEXTflex[1,][4:6])

testpheno<-Pheno1000[Pheno1000$Kit=="Fivepercent",]$Batch

head(fits$Fivepercent$p.value)
t.test(split_kit_thresh$Fivepercent[4,][1:3],split_kit_thresh$Fivepercent[4,][4:6])
summary(lm(t(split_kit_thresh$Fivepercent[4,])~testpheno))

head(fits$NEXTflex$p.value)
t.test(split_kit_thresh$NEXTflex[4,][1:3],split_kit_thresh$NEXTflex[4,][4:6])

```

