---
title: "Synth_analysis"
author: "carriewright"
date: "12/19/2017"
output:
  html_document:
    code_folding: hide
---
#########################################################
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r}
library(here)
load(here("normalized_synth.rmd"))
```


###FUNCTIONS to get ttests results and output nicely
```{r, echo = TRUE, eval=TRUE}
library(dplyr)
get_test_names <- function(data){
  test_names <<- data.frame(combn(names(data), m= 2))
}

get_test_results<- function(data,test_names) {
  tresults<<-list()
  tested_names1<<-list()
  tested_names2<<-list()
  for(i in names(test_names)){
    Kit1<-data.frame(select(data, colnames(data)[colnames(data) %in% test_names[i][1,]]))
    Kit2<-data.frame(select(data, colnames(data)[colnames(data) %in% test_names[i][2,]]))
    tested_names1[[i]]<<-colnames(Kit1)
    tested_names2[[i]]<<-colnames(Kit2)
    colnames(Kit1)<-c("error")
    colnames(Kit2)<-c("error")
    tresults[[i]]<<-t.test(x=Kit1$error, y=Kit2$error, paired = TRUE) ### may have messed things up adding paired = TRUE previously had more ))
    tested_kits <<-paste0(tested_names1, "&", tested_names2)
  }
}

get_ttestStats<- function(x) {
  c(t =format(x$statistic, digits = 2),
    df = format(x$parameter, digits = 0),
    p.value = format(x$p.value, scientific = TRUE, digits = 2),
    bonferroni_thresh = format(.05/length(test_names), digits = 2),
    sig = ifelse(x$p.value<(.05/length(test_names)), "yes", "no"),
    t.es.g = tes(x$statistic, n.1 = 962, n.2 = 962)$g,
    t.es.OR =tes(x$statistic, n.1 = 962, n.2 = 962)$OR)
}


get_perc_diff <-function(data) {
  percresults<<-list()
  tested_names1<<-list()
  tested_names2<<-list()
  tested_kits<<-list()
  for(i in names(test_names)){
    percresults[[i]]<<-((colMeans(data)[ which(names(colMeans(data))==test_names[i][1,])]-colMeans(data)[ which(names(colMeans(data))==test_names[i][2,])])/ colMeans(data)[ which(names(colMeans(data))==test_names[i][2,])])*100
    tested_names1[[i]]<<-test_names[i][1,]
    tested_names2[[i]]<<-test_names[i][2,]
    tested_kits[[i]] <<-paste0(tested_names1[[i]], "&", tested_names2[[i]])
    }
}



```


###Callfunctions on the data to get stats on comparisons
```{r, eval=TRUE}
library(reshape2)
library(compute.es)
library(sjstats)

get_test_names(data = error_synth)
get_test_results(test_names = test_names, data = error_synth)
ttestStats<-data.frame(lapply(tresults, get_ttestStats))
colnames(ttestStats)<-tested_kits
ttestStats

synth <-melt(error_synth)
fit = lm(synth$value ~ synth$variable)
anova(fit)
sjstats::anova_stats(aov(fit)) # get effect size

#calculate percent differences
get_perc_diff(data = error_synth)
perc_stats<-data.frame(percresults)
colnames(perc_stats)<-tested_kits
perc_stats

sapply(error_synth, mean)
```

#### Main Plot###########
```{r}
library(jaffelab)
library(ggplot2)
library(ggpubr)
library(ggsignif)


error_synth$miRNA <-rownames(error_synth) # add miRNA info
synth<- melt(error_synth) # reshape the data
synth$miRNA <-jaffelab::ss(synth$miRNA, "-" ,slot =2)# grab second part of the name

plot1000<-ggplot(data = synth, aes(x = variable, y = value, color= variable, label = miRNA))+geom_jitter(aes(fill = variable, alpha = 1), width= .3) +geom_boxplot( outlier.shape = NA, notch = TRUE, color = "black", position = position_dodge(1))+
  labs(y = "Error from the mean")+
   theme(axis.title.x = element_text(size =0), 
        plot.title = element_text(size = 18, face = "bold", hjust = 0.1), 
        axis.text.x = element_text(size = 15, colour = "Black", angle = 20, hjust = 1),
        axis.text.y = element_text(size = 15), 
        axis.title.y = element_text(size =18))
pdf(file =here("Figures/Raw_plots/Fig.4.a.tall.pdf"),width=6,height=4)
plot1000    +  theme(legend.position = "none")+ labs(y = "Absolute error from the mean", title = "Error of Synthetic Sequence Detection") + stat_compare_means(method = "anova", label.sep = ", " )
dev.off()
```

Are high error miRNAs the same across methods?
```{r}
library(ggrepel)

ranks_error<-data.frame(sapply(-error_synth[1:6], rank, ties.method = c("random")))#ranked so 1 is the highest error
ranks_error$miRNA<-error_synth$miRNA

rownames(ranks_error)<-ranks_error$miRNA
Clontech_ranks <-(ranks_error[grep("Clontech", colnames(ranks_error))])
Illumina_ranks <-(ranks_error[grep("Illumina", colnames(ranks_error))])
NEB_ranks <-(ranks_error[grep("NEB", colnames(ranks_error))])
NEXTflex_ranks <-(ranks_error[grep("NEXTflex", colnames(ranks_error))])
Deduped_ranks <-(ranks_error[grep("Deduped", colnames(ranks_error))])
Fivepercent_ranks <-(ranks_error[grep("Fivepercent", colnames(ranks_error))])
ranked_miRNA<-list()

Clontech_miRNAs <- data.frame("Clontech" =rownames(ranks_error)[order(Clontech_ranks$Clontech)])
NEXTflex_miRNAs <- data.frame("NEXTflex" =rownames(ranks_error)[order(NEXTflex_ranks$NEXTflex)]) 
Deduped_miRNAs <- data.frame("Deduped" =rownames(ranks_error)[order(Deduped_ranks$Deduped)]) 
Fivepercent_miRNAs <- data.frame("Fivepercent" =rownames(ranks_error)[order(Fivepercent_ranks$Fivepercent)])
NEB_miRNAs <- data.frame("NEB" =rownames(ranks_error)[order(NEB_ranks$NEB)])
Illumina_miRNAs <- data.frame("Illumina"=rownames(ranks_error)[order(Illumina_ranks$Illumina)])
ranked_miRNA <-data.frame(Clontech_miRNAs, Illumina_miRNAs, NEB_miRNAs, NEXTflex_miRNAs,  Deduped_miRNAs, Fivepercent_miRNAs)


ranks_error_clontech <- ranks_error[order(ranks_error$Clontech),]
write.csv(ranks_error, here("Supplement/syth_acc_ranks.csv"))

library(DescTools)

KendallW(ranks_error, correct = FALSE, test = TRUE)# the ranks are not similar for the methods...
KendallW(ranks_error[1:2], correct = FALSE, test = TRUE)# Clontech and Illumina
KendallW(ranks_error[c(1,3)], correct = FALSE, test = TRUE)# Clontech and NEB
KendallW(ranks_error[c(1,4)], correct = FALSE, test = TRUE)# Clontech and NEXTflex # these are very similar
KendallW(ranks_error[c(1,5)], correct = FALSE, test = TRUE)# Clontech and Deduped
KendallW(ranks_error[c(1,6)], correct = FALSE, test = TRUE)# Clontech and Fivepercent

KendallW(ranks_error[2:3], correct = FALSE, test = TRUE)# Illumina and NEB
KendallW(ranks_error[c(2,4)], correct = FALSE, test = TRUE)# Illumina and NEXTflex
KendallW(ranks_error[c(2,5)], correct = FALSE, test = TRUE)# Illumina and Deduped # these are very similar
KendallW(ranks_error[c(2,6)], correct = FALSE, test = TRUE)# Illumina and Fivepercent

KendallW(ranks_error[c(3,4)], correct = FALSE, test = TRUE)# NEB and NEXTflex
KendallW(ranks_error[c(3,5)], correct = FALSE, test = TRUE)# NEB and Deduped
KendallW(ranks_error[c(3,6)], correct = FALSE, test = TRUE)# NEBand Fivepercent # these are very similar

KendallW(ranks_error[c(4,5)], correct = FALSE, test = TRUE)# NEXTflex and Deduped
KendallW(ranks_error[c(4,6)], correct = FALSE, test = TRUE)# NEXTflex and Fivepercent
KendallW(ranks_error[c(5,6)], correct = FALSE, test = TRUE)# Deduped and Fivepercent
```

CATplots
```{r}
library(ffpe)

#rel to Clontech
library(RColorBrewer)
trop = cols <- brewer.pal(9, "Set1")
pdf(file =here("Supplement/Figures/synth_rank_to_Clontech.pdf"),width=10,height=8, onefile=FALSE)
forcatplot_1000 <- list(ranks_error$Clontech, ranks_error$Illumina, ranks_error$NEB, ranks_error$NEXTflex, ranks_error$Deduped, ranks_error$Fivepercent)
forcatplot_1000[[7]] <- c(rep(0,962))
forcatplot_1000[[8]] <- c(ranks_error$Clontech[1:20],rep(0,942)) #example of perfect concordance of just the first 20 and then no concordance

catplots <-list()
for(i in 1:8){
  catplots[[i]] = CATplot(forcatplot_1000[[i]],forcatplot_1000[[1]],make.plot=F)
}
par(mar=c(5,5,5,5))
plot(catplots[[2]],ylim=c(0,1),col=trop[1],lwd=3,type="l",ylab="Concordance Between Methods",xlab="Rank", xlim=c(1,962), cex.lab=2, cex.axis=2)
lines(catplots[[3]],col=trop[2],lwd=3,lty=2)
lines(catplots[[4]],col=trop[3],lwd=3)
lines(catplots[[5]],col=trop[4],lwd=3,lty=3)
lines(catplots[[6]],col=trop[5],lwd=3,lty=1)
lines(catplots[[1]],col=trop[7],lwd=3,lty=3)
lines(catplots[[7]], col=trop[9],lwd=3)
lines(catplots[[8]], col=trop[3],lwd=3, lty =3)
legend(600,0.55,legend=c("Clontech_vs_Illumina","Clontech_vs_NEB", "Clontech_vs_NEXTflex","Clontech_vs_Deduped","Clontech_vs_Fivepercent", "Perfect_concordance", "No_concordance","Just_top_concordance"),col=trop[c(1,2,3,4,5,7,9,3)],lty=c(1,2,1,3,1,3,1,3),lwd=3)
dev.off()

#rel to NEXTflex
pdf(file =here("Supplement/Figures/synth_rank_to_NEXTflex.pdf"),width=10,height=8, onefile=FALSE)
forcatplot_1000 <- list( ranks_error$NEXTflex,ranks_error$Illumina, ranks_error$NEB, ranks_error$Clontech, ranks_error$Deduped, ranks_error$Fivepercent)
forcatplot_1000[[7]] <- c(rep(0,962)) #allzeros for zero concordance example
forcatplot_1000[[8]] <- c(ranks_error$NEXTflex[1:20],rep(0,942)) #example of perfect concordance of just the first 20 and then no concordance

catplots <-list()
for(i in 1:8){
  catplots[[i]] = CATplot(forcatplot_1000[[i]],forcatplot_1000[[1]],make.plot=F)
}
par(mar=c(5,5,5,5))
plot(catplots[[2]],ylim=c(0,1),col=trop[1],lwd=3,type="l",ylab="Concordance Between Methods",xlab="Rank", xlim=c(1,962), cex.lab=2, cex.axis=2)
lines(catplots[[3]],col=trop[2],lwd=3,lty=2)
lines(catplots[[4]],col=trop[3],lwd=3)
lines(catplots[[5]],col=trop[4],lwd=3,lty=3)
lines(catplots[[6]],col=trop[5],lwd=3,lty=1)
lines(catplots[[1]],col=trop[7],lwd=3,lty=3)
lines(catplots[[7]], col=trop[9],lwd=3)
lines(catplots[[8]], col=trop[3],lwd=3, lty =3)
legend(600,0.55,legend=c("NEXTflex_vs_Illumina","NEXTflex_vs_NEB", "NEXTflex_vs_Clontech","NEXTflex_vs_Deduped","NEXTflex_vs_Fivepercent", "Perfect_concordance", "No_concordance", "Just_top_concordance"),col=trop[c(1,2,3,4,5,7,9,3)],lty=c(1,2,1,3,1,3,1,3),lwd=3)
dev.off()

#1000ng -rel to Illumina
pdf(file =here("Supplement/Figures/synth_rank_to_Illumina.pdf"),width=10,height=8, onefile=FALSE)
forcatplot_1000 <- list(ranks_error$Illumina,ranks_error$Clontech, ranks_error$NEB, ranks_error$NEXTflex, ranks_error$Deduped, ranks_error$Fivepercent)
forcatplot_1000[[7]] <- c(rep(0,962))
forcatplot_1000[[8]] <- c(ranks_error$Illumina[1:20],rep(0,942)) #example of perfect concordance of just the first 20 and then no concordance

catplots <-list()
for(i in 1:8){
  catplots[[i]] = CATplot(forcatplot_1000[[i]],forcatplot_1000[[1]],make.plot=F)
}
par(mar=c(5,5,5,5))
plot(catplots[[2]],ylim=c(0,1),col=trop[1],lwd=3,type="l",ylab="Concordance Between Methods",xlab="Rank", xlim=c(1,962),  cex.lab=2, cex.axis=2)
lines(catplots[[3]],col=trop[2],lwd=3,lty=2)
lines(catplots[[4]],col=trop[3],lwd=3)
lines(catplots[[5]],col=trop[4],lwd=3,lty=3)
lines(catplots[[6]],col=trop[5],lwd=3,lty=1)
lines(catplots[[1]],col=trop[7],lwd=3,lty=3)
lines(catplots[[7]], col=trop[9],lwd=3)
lines(catplots[[8]], col=trop[3],lwd=3, lty =3)
legend(600,0.55,legend=c("Illumina_vs_Clontech","Illumina_vs_NEB", "Illumina_vs_NEXTflex","Illumina_vs_Deduped","Illumina_vs_Fivepercent", "Perfect_concordance", "No_concordance", "Just_top_concordance"),col=trop[c(1,2,3,4,5,7,9,3)],lty=c(1,2,1,3,1,3,1,3),lwd=3)
dev.off()

#1000ng -rel to NEB
pdf(file =here("Supplement/Figures/synth_rank_to_NEB.pdf"),width=10,height=8, onefile=FALSE)
forcatplot_1000 <- list(ranks_error$NEB,ranks_error$Clontech,ranks_error$Illumina, ranks_error$NEXTflex, ranks_error$Deduped, ranks_error$Fivepercent)
forcatplot_1000[[7]] <- c(rep(0,962))
forcatplot_1000[[8]] <- c(ranks_error$NEB[1:20],rep(0,942)) #example of perfect concordance of just the first 20 and then no concordance

catplots <-list()
for(i in 1:8){
  catplots[[i]] = CATplot(forcatplot_1000[[i]],forcatplot_1000[[1]],make.plot=F)
}
par(mar=c(5,5,5,5))
plot(catplots[[2]],ylim=c(0,1),col=trop[1],lwd=3,type="l",ylab="Concordance Between Methods",xlab="Rank", xlim=c(1,962), cex.lab=2, cex.axis=2)
lines(catplots[[3]],col=trop[2],lwd=3,lty=2)
lines(catplots[[4]],col=trop[3],lwd=3)
lines(catplots[[5]],col=trop[4],lwd=3,lty=3)
lines(catplots[[6]],col=trop[5],lwd=3,lty=1)
lines(catplots[[1]],col=trop[7],lwd=3,lty=3)
lines(catplots[[7]], col=trop[9],lwd=3)
lines(catplots[[8]], col=trop[3],lwd=3, lty =3)
legend(600,0.55,legend=c("NEB_vs_Clontech","NEB_vs_Illumina", "NEB_vs_NEXTflex","NEB_vs_Deduped","NEB_vs_Fivepercent", "Perfect_concordance","No_concordance", "Just_top_concordance"),col=trop[c(1,2,3,4,5,7,9,3)],lty=c(1,2,1,3,1,3,1,3),lwd=3)
dev.off()

#1000ng -rel to Deduped
pdf(file =here("Supplement/Figures/synth_rank_to_Deduped.pdf"),width=10,height=8, onefile=FALSE)
forcatplot_1000 <- list(ranks_error$Deduped,ranks_error$Clontech,ranks_error$Illumina, ranks_error$NEB, ranks_error$NEXTflex, ranks_error$Fivepercent)
forcatplot_1000[[7]] <- c(rep(0,962))
forcatplot_1000[[8]] <- c(ranks_error$Deduped[1:20],rep(0,942)) #example of perfect concordance of just the first 20 and then no concordance

catplots <-list()
for(i in 1:8){
  catplots[[i]] = CATplot(forcatplot_1000[[i]],forcatplot_1000[[1]],make.plot=F)
}
par(mar=c(5,5,5,5))
plot(catplots[[2]],ylim=c(0,1),col=trop[1],lwd=3,type="l",ylab="Concordance Between Methods",xlab="Rank", xlim=c(1,962),cex.lab=2, cex.axis=2)
lines(catplots[[3]],col=trop[2],lwd=3,lty=2)
lines(catplots[[4]],col=trop[3],lwd=3)
lines(catplots[[5]],col=trop[4],lwd=3,lty=3)
lines(catplots[[6]],col=trop[5],lwd=3,lty=1)
lines(catplots[[1]],col=trop[7],lwd=3,lty=3)
lines(catplots[[7]], col=trop[9],lwd=3)
lines(catplots[[8]], col=trop[3],lwd=3, lty =3)
legend(600,0.55,legend=c("Deduped_vs_Clontech","Deduped_vs_Illumina","Deduped_vs_NEB", "Deduped_vs_NEXTflex","Deduped_vs_Fivepercent", "Perfect_concordance","No_concordance", "Just_top_concordance"),col=trop[c(1,2,3,4,5,7,9,3)],lty=c(1,2,1,3,1,3,1,3),lwd=3)
dev.off()

#1000ng -rel to Fivepercent
pdf(file =here("Supplement/Figures/synth_rank_to_Fivepercent.pdf"),width=10,height=8, onefile=FALSE)
forcatplot_1000 <- list(ranks_error$Fivepercent,ranks_error$Clontech,ranks_error$Illumina, ranks_error$NEB, ranks_error$NEXTflex, ranks_error$Deduped)
forcatplot_1000[[7]] <- c(rep(0,962))
forcatplot_1000[[8]] <- c(ranks_error$Fivepercent[1:20],rep(0,942)) #example of perfect concordance of just the first 20 and then no concordance


catplots <-list()
for(i in 1:8){
  catplots[[i]] = CATplot(forcatplot_1000[[i]],forcatplot_1000[[1]],make.plot=F)
}
par(mar=c(5,5,5,5))
plot(catplots[[2]],ylim=c(0,1),col=trop[1],lwd=3,type="l",ylab="Concordance Between Methods",xlab="Rank", xlim=c(1,962),  cex.lab=2, cex.axis=2)
lines(catplots[[3]],col=trop[2],lwd=3,lty=2)
lines(catplots[[4]],col=trop[3],lwd=3)
lines(catplots[[5]],col=trop[4],lwd=3,lty=3)
lines(catplots[[6]],col=trop[5],lwd=3,lty=1)
lines(catplots[[1]],col=trop[7],lwd=3,lty=3)
lines(catplots[[7]], col=trop[9],lwd=3)
lines(catplots[[8]], col=trop[3],lwd=3, lty =3)
legend(600,0.55,legend=c("Fivepercent_vs_Clontech","Fivepercent_vs_Illumina","Fivepercent_vs_NEB", "Fivepercent_vs_NEXTflex","Fivepercent_vs_Deduped", "Perfect_concordance", "No_concordance", "Just_top_concordance"),col=trop[c(1,2,3,4,5,7,9,3)],lty=c(1,2,1,3,1,3,1,3),lwd=3)
dev.off()

```



####################Sequence Feature Plots ######################################
relative consistency
```{r}
errorData_toplot<-log2(miRge_synth+1)
get_perc<-function(x) {(x/mean(x))*100}
errorData_toplot<-data.frame(lapply(errorData_toplot, get_perc))
```

GC line plot
```{r}
errorGC <-cbind(seqs$GC, errorData_toplot)
errorGC$`seqs$GC`<-as.factor(errorGC$`seqs$GC`)
errorGC<-melt(errorGC)
errorGC$`seqs$GC`<-as.numeric(as.character(errorGC$`seqs$GC`))
colnames(errorGC)<-c("GC_Content", "Kit", "expression")
#errorGC$Kit <- factor(errorGC$Kit, levels =c("Clontech","Illumina","NEB","NEXTflex","Deduped", "Fivepercent"))
  plot1002<<-ggplot(data = errorGC, aes(x = GC_Content, y = expression, color= Kit)) +geom_point(aes(color = Kit))+
  theme(axis.title.x = element_text(size =20), 
        plot.title = element_text(size = 18, face = "bold", hjust = 0.1), 
        axis.text.x = element_text(size = 25),
        axis.text.y = element_text(size = 20), 
        axis.title.y = element_text(size =20))
        
  plot1002 +labs(x = "GC_Content", y = "Relative Expression to mean", title = "Consistency of detection across GC_content") + stat_smooth(method = loess) 

```


#####Heatmap############

Last and First good Plots of expression relative to the mean!
```{r, eval = TRUE}
library(pheatmap)
###get seq info
lastStuff<-function(str, n){result <-substr(str,(nchar(str)+1)-n,nchar(str))}
seqs_last <- data.frame(x =lastStuff(str=seqs$RNA, 2))####uncomment to get last n bases
rownames(seqs_last)<-seqs$name
seqs_first <-data.frame(x =strtrim(seqs$RNA, c(2)))###uncomment to get first n bases and comment next line
rownames(seqs_first)<-seqs$name

errorData_toplot<-log2(miRge_synth+1)
get_perc<-function(x) {(x/mean(x))*100}
errorData_toplot<-data.frame(lapply(errorData_toplot, get_perc))
errorLast<-cbind(seqs_last, errorData_toplot)
errorFirst<-cbind(seqs_first, errorData_toplot)



####get Breaks
aggdata <-aggregate(errorFirst[-1], by=list(errorFirst$x), FUN=mean)
rownames(aggdata) <- aggdata$Group.1
aggdata<-aggdata[which(colnames(aggdata)!="Group.1")]
sorted_aggdata <- aggdata[match(rownames(aggdata), sort(rownames(aggdata))),]  
sorted_aggdata <<- sorted_aggdata
paletteLength <- 10

myBreaks_below<-seq(to=max(sorted_aggdata[sorted_aggdata<100]), from = round(min(sorted_aggdata))-3, length.out = paletteLength*abs(min(sorted_aggdata))/10)
myBreaks_above<-seq(to=round(max(sorted_aggdata))+3, from = min(sorted_aggdata[sorted_aggdata>100]), length.out = paletteLength*(max(sorted_aggdata))/10)
myBreaks_first <- c(myBreaks_below, myBreaks_above)

aggdata <-aggregate(errorLast[-1], by=list(errorLast$x), FUN=mean)
rownames(aggdata) <- aggdata$Group.1
aggdata<-aggdata[which(colnames(aggdata)!="Group.1")]
sorted_aggdata <- aggdata[match(rownames(aggdata), sort(rownames(aggdata))),]  
sorted_aggdata <<- sorted_aggdata
paletteLength <- paletteLength

myBreaks_below<-seq(to=max(sorted_aggdata[sorted_aggdata<100]), from = round(min(sorted_aggdata))-3, length.out = paletteLength*abs(min(sorted_aggdata))/10)
myBreaks_above<-seq(to=round(max(sorted_aggdata))+3, from = min(sorted_aggdata[sorted_aggdata>100]), length.out = paletteLength*(max(sorted_aggdata))/10)
myBreaks_last <- c(myBreaks_below, myBreaks_above)

myBreaks<-append(myBreaks_first,myBreaks_last[which(myBreaks_last>max(myBreaks_first))])
myBreaks<-append(myBreaks_first[which(myBreaks_first<min(myBreaks))], myBreaks)
myBreaks<-append(myBreaks_last[which(myBreaks_last<min(myBreaks))], myBreaks)
myBreaks<-append(myBreaks,myBreaks_last[which(myBreaks_last>max(myBreaks))])

myColorbelow<-colorRampPalette(c("blue","white"))(length(which(myBreaks<100))) ### change for white 
myColorabove<-colorRampPalette(c("white","red"))(length(which(myBreaks>100)))### change for white
myColor<-c(myColorbelow, myColorabove)
###################

```

relative percentage heatmaps
```{r}
library(pheatmap)
make_heatmap <-function(Data, title){
aggdata <-aggregate(Data[-1], by=list(Data$x), FUN=mean)
rownames(aggdata) <- aggdata$Group.1
aggdata<-aggdata[which(colnames(aggdata)!="Group.1")]
sorted_aggdata <- aggdata[match(rownames(aggdata), sort(rownames(aggdata))),]  

pheatmap(sorted_aggdata, color = myColor, breaks =myBreaks, cluster_cols = FALSE, cluster_rows = TRUE, main = title)
}
pdf(file =here("Supplement/Figures/synth_errorFirst_bases_heatmap.pdf"),width=12,height=6, onefile=FALSE)
make_heatmap(Data = errorFirst, title = "Consistency of expression of sequences with different first 2 bases")
dev.off()

pdf(file =here("Supplement/Figures/synth_errorLast_bases_heatmap.pdf"),width=12,height=6, onefile=FALSE)
make_heatmap(Data = errorLast, title = "Consistency of expression of sequences with different last 2 bases")
dev.off()


firstdata <-melt(errorFirst)
pdf(file =here("Supplement/Figures/synth_errorFirstbases_boxplot.pdf"),width=18,height=6, onefile=FALSE)
ggplot(data = firstdata, aes(x=x, y = value, fill = variable)) + geom_jitter() + geom_boxplot(varwidth = TRUE)+facet_grid(~variable)+theme(legend.position="none")+labs(y = "Expression relative to the mean", title = "Consistency of synthetic sequence detection across different first 2 bases", x = NULL,   theme(axis.title.x = element_text(size =0),
plot.title = element_text(size = 100, face = "bold", hjust = 0.5),axis.text.x = element_text(size = 40),axis.text.y = element_text(size = 100),axis.title.y = element_text(size =15),legend.text=element_text(size=100), strip.text.x = element_text(size =100)))
dev.off()


lastdata <-melt(errorLast)
pdf(file =here("Supplement/Figures/synth_errorLastbases_boxplot.pdf"),width=18,height=4, onefile=FALSE)
ggplot(data = lastdata, aes(x=x, y = value, fill = variable))  + geom_jitter()+geom_boxplot(varwidth = TRUE)+facet_grid(~variable)+theme(legend.position="none") +labs(y = "Expression relative to the mean", title = "Consistency of synthetic sequence detection across different last 2 bases", x = NULL,   theme(axis.title.x = element_text(size =0),
plot.title = element_text(size = 100, face = "bold", hjust = 0.5),axis.text.x = element_text(size = 40),axis.text.y = element_text(size = 100),axis.title.y = element_text(size =15),legend.text=element_text(size=100), strip.text.x = element_text(size =100)))
dev.off()
```






Length based on log2 expression +1
```{r}
library(ggpubr)
errorData_toplot<-log2(miRge_synth+1)
errorData_toplot<-data.frame(lapply(errorData_toplot, get_perc))
errorLength<-as.data.frame(cbind(seqs$length, errorData_toplot))
colnames(errorLength) <- c("length","Clontech","Illumina","NEB","NEXTflex","Deduped", "Fivepercent")
errorGC<-as.data.frame(cbind(round(seqs$GC, digits = 1), errorData_toplot))
colnames(errorGC) <- c("GC","Clontech","Illumina","NEB","NEXTflex","Deduped", "Fivepercent")

aggdata <-aggregate(errorLength, by=list(errorLength$length), FUN=mean)
rownames(aggdata) <- aggdata$Group.1
aggdata<-aggdata[which(colnames(aggdata)!="Group.1"&colnames(aggdata)!="length")]
paletteLength <- 10

sorted_aggdata <- aggdata[match(rownames(aggdata), sort(rownames(aggdata))),]  

myBreaks_below<-seq(to=max(sorted_aggdata[sorted_aggdata<100]), from = round(min(sorted_aggdata))-3, length.out = paletteLength*abs(min(sorted_aggdata))/10)

myBreaks_above<-seq(to=round(max(sorted_aggdata))+3, from = min(sorted_aggdata[sorted_aggdata>100]), length.out = paletteLength*(max(sorted_aggdata))/10)
myBreaks_last <- c(myBreaks_below, myBreaks_above)

myBreaks<-append(myBreaks_first,myBreaks_last[which(myBreaks_last>max(myBreaks_first))])
myBreaks<-append(myBreaks_first[which(myBreaks_first<min(myBreaks))], myBreaks)
myBreaks<-append(myBreaks_last[which(myBreaks_last<min(myBreaks))], myBreaks)
myBreaks<-append(myBreaks,myBreaks_last[which(myBreaks_last>max(myBreaks))])

myColorbelow<-colorRampPalette(c("blue","white"))(length(which(myBreaks<100))) ### change for white 
myColorabove<-colorRampPalette(c("white","red"))(length(which(myBreaks>100)))### change for white
myColor<-c(myColorbelow, myColorabove)

pdf(file =here("Supplement/Figures/synth_errorLength_heatmap.pdf"),width=12,height=6, onefile=FALSE)
pheatmap(aggdata, color=myColor, breaks=myBreaks, main = "Length", cluster_cols = FALSE, cluster_rows = FALSE)
ggplot(melt(t(sorted_aggdata)), aes(x=Var2, y = value, fill = Var1)) + geom_bar(stat = "identity")+facet_grid(~Var1)+theme(legend.position="none")+coord_cartesian(ylim=c(min(myBreaks-10), max(myBreaks+10)))+coord_cartesian(ylim=c(60, 140))
dev.off()
lengthplot <-errorLength
lengthplot$length <-factor(lengthplot$length)
pdf(file =here("Supplement/Figures/synth_errorLength_boxplot.pdf"),width=12,height=4, onefile=FALSE)
ggplot(data = melt(lengthplot), aes(x=length, y = value, fill = variable)) + geom_jitter()+geom_boxplot(varwidth = TRUE)+facet_grid(~variable) +theme(strip.text.x = element_text(size = 14),axis.text.x = element_text(size = 14), axis.text.y = element_text(size = 14), axis.title.x = element_text(size = 18, angle = 60),axis.title.y = element_text(size = 18),title = element_text(size = 24), legend.position="none") +labs(y = "Percent expression relative to the mean", title = "Consistency of synthetic sequence detection across lengths", x = "Sequence Length") +geom_smooth(method = "loess", se=TRUE, color="black", aes(group=1, fill = variable)) + theme(axis.text.x = element_text(angle =60, hjust = 1))
dev.off()
```



GC
```{r}
errorData_toplot<-log2(miRge_synth+1)
errorData_toplot<-data.frame(lapply(errorData_toplot, get_perc))

errorGC<-as.data.frame(cbind(round(seqs$GC, digits = 1), errorData_toplot))
colnames(errorGC) <- c("GC", "Clontech", "Illumina", "NEB", "NEXTflex", "Deduped", "Fivepercent")

aggdata <-aggregate(errorGC, by=list(errorGC$GC), FUN=mean)
rownames(aggdata) <- aggdata$Group.1
aggdata<-aggdata[which(colnames(aggdata)!="Group.1"&colnames(aggdata)!="GC")]
sorted_aggdata <- aggdata[match(rownames(aggdata), sort(rownames(aggdata))),]  
paletteLength <- 10

myBreaks_below<-seq(to=max(sorted_aggdata[sorted_aggdata<100]), from = round(min(sorted_aggdata))-3, length.out = paletteLength*abs(min(sorted_aggdata))/10)

myBreaks_above<-seq(to=round(max(sorted_aggdata))+3, from = min(sorted_aggdata[sorted_aggdata>100]), length.out = paletteLength*(max(sorted_aggdata))/10)
myBreaks_last <- c(myBreaks_below, myBreaks_above)

myBreaks<-append(myBreaks_first,myBreaks_last[which(myBreaks_last>max(myBreaks_first))])
myBreaks<-append(myBreaks_first[which(myBreaks_first<min(myBreaks))], myBreaks)
myBreaks<-append(myBreaks_last[which(myBreaks_last<min(myBreaks))], myBreaks)
myBreaks<-append(myBreaks,myBreaks_last[which(myBreaks_last>max(myBreaks))])

myColorbelow<-colorRampPalette(c("blue","white"))(length(which(myBreaks<100))) ### change for white 
myColorabove<-colorRampPalette(c("white","red"))(length(which(myBreaks>100)))### change for white
myColor<-c(myColorbelow, myColorabove)

pdf(file =here("Supplement/Figures/synth_errorGC_heatmap.pdf"),width=12,height=8, onefile=FALSE)
pheatmap(sorted_aggdata, color=myColor, breaks=myBreaks, main = "GC", cluster_cols = FALSE, cluster_rows = FALSE)
dev.off()
pdf(file =here("Supplement/Figures/synth_errorGC_bar.pdf"),width=12,height=8, onefile=FALSE)
ggplot(melt(t(sorted_aggdata)), aes(x=Var2, y = value, fill = Var1)) + geom_bar(stat = "identity")+facet_grid(~Var1)+theme(legend.position="none")+coord_cartesian(ylim=c(min(myBreaks-10), max(myBreaks+10)))
dev.off()
GCplot <-errorGC

GCplot$GC <-factor(GCplot$GC)
pdf(file =here("Supplement/Figures/synth_errorGC_box.pdf"),width=12,height=8, onefile=FALSE)
ggplot(data = melt(GCplot), aes(x=GC, y = value, fill = variable)) + geom_jitter()+ geom_boxplot(varwidth = TRUE)+facet_grid(~variable)+theme(legend.position="none")+geom_smooth(method = "loess", se=TRUE, color="black", aes(group=1, fill = variable)) + theme(axis.text.x = element_text(angle =60, hjust = 1))
dev.off()
```





Fold
```{r}
errorData_toplot<-log2(miRge_synth+1)
errorData_toplot<-(errorData_toplot /colMeans(errorData_toplot))*100

errorFoldG<-as.data.frame(cbind(round(seqs$FoldG, digits = 0), errorData_toplot))
colnames(errorFoldG) <- c("FoldG", "Clontech", "Illumina", "NEB", "NEXTflex", "Deduped", "Fivepercent")

aggdata <-aggregate(errorFoldG, by=list(errorFoldG$FoldG), FUN=mean)
rownames(aggdata) <- aggdata$Group.1
aggdata<-aggdata[which(colnames(aggdata)!="Group.1"&colnames(aggdata)!="FoldG")]
 
sorted_aggdata <-aggdata
paletteLength <- 10

myBreaks_below<-seq(to=max(sorted_aggdata[sorted_aggdata<100]), from = round(min(sorted_aggdata))-3, length.out = paletteLength*abs(min(sorted_aggdata))/10)

myBreaks_above<-seq(to=round(max(sorted_aggdata))+3, from = min(sorted_aggdata[sorted_aggdata>100]), length.out = paletteLength*(max(sorted_aggdata))/10)
myBreaks_last <- c(myBreaks_below, myBreaks_above)

myBreaks<-append(myBreaks_first,myBreaks_last[which(myBreaks_last>max(myBreaks_first))])
myBreaks<-append(myBreaks_first[which(myBreaks_first<min(myBreaks))], myBreaks)
myBreaks<-append(myBreaks_last[which(myBreaks_last<min(myBreaks))], myBreaks)
myBreaks<-append(myBreaks,myBreaks_last[which(myBreaks_last>max(myBreaks))])

myColorbelow<-colorRampPalette(c("blue","white"))(length(which(myBreaks<100))) ### change for white 
myColorabove<-colorRampPalette(c("white","red"))(length(which(myBreaks>100)))### change for white
myColor<-c(myColorbelow, myColorabove)

pdf(file =here("Supplement/Figures/synth_errorfold_heatmap.pdf"),width=12,height=8, onefile=FALSE)
pheatmap(sorted_aggdata, color=myColor, breaks=myBreaks, main = "FoldG", cluster_cols = FALSE, cluster_rows = FALSE)
pdf(file =here("Supplement/Figures/synth_errorfold_bar.pdf"),width=12,height=8, onefile=FALSE)
ggplot(melt(t(sorted_aggdata)), aes(x=Var2, y = value, fill = Var1)) + geom_bar(stat = "identity")+facet_grid(~Var1)+theme(legend.position="none")+coord_cartesian(ylim=c(min(myBreaks-10), max(myBreaks+10)))
FoldGplot <-errorFoldG
FoldGplot$FoldG <-factor(FoldGplot$FoldG)
pdf(file =here("Supplement/Figures/synth_errorfold_box.pdf"),width=12,height=8, onefile=FALSE)
ggplot(data = melt(FoldGplot), aes(x=FoldG, y = value, fill = variable)) + geom_boxplot(varwidth = TRUE)+facet_grid(~variable)+theme(legend.position="none") +geom_smooth(method = "loess", se=TRUE, color="black", aes(group=1, fill = variable)) + theme(axis.text.x = element_text(angle =60, hjust = 1))

table(round(seqs$FoldG))

```




Repeats
```{r}
TTTT<-sapply(gregexpr("TTTT", seqs$x), function(x) sum(x != -1))
GGGG<-sapply(gregexpr("GGGG", seqs$x), function(x) sum(x != -1))
AAAA<-sapply(gregexpr("AAAA", seqs$x), function(x) sum(x != -1))
CCCC<-sapply(gregexpr("CCCC", seqs$x), function(x) sum(x != -1))
patterns <- c("TT", "GG", "CC", "AA")
duplets <- sapply(gregexpr(paste(patterns,collapse="|"), 
                        seqs$x), function(x) sum(x != -1))
anyT<-sapply(gregexpr("T", seqs$x), function(x) sum(x != -1))
anyG<-sapply(gregexpr("G", seqs$x), function(x) sum(x != -1))
anyC<-sapply(gregexpr("C", seqs$x), function(x) sum(x != -1))
anyA<-sapply(gregexpr("A", seqs$x), function(x) sum(x != -1))
```

Duplets
```{r}
errorData_toplot<-log2(miRge_synth+1)
errorData_toplot<-(errorData_toplot /colMeans(errorData_toplot))*100

error<-as.data.frame(cbind(duplets, errorData_toplot))
colnames(error) <- c("duplets", "Clontech", "Illumina", "NEB", "NEXTflex", "Deduped", "Fivepercent")

aggdata <-aggregate(error, by=list(error$duplets), FUN=mean)
rownames(aggdata) <- aggdata$Group.1
aggdata<-aggdata[which(colnames(aggdata)!="Group.1"&colnames(aggdata)!="FoldG")]
sorted_aggdata <-aggdata
paletteLength <- 10

myBreaks_below<-seq(to=max(sorted_aggdata[sorted_aggdata<100]), from = round(min(sorted_aggdata))-3, length.out = paletteLength*abs(min(sorted_aggdata))/10)

myBreaks_above<-seq(to=round(max(sorted_aggdata))+3, from = min(sorted_aggdata[sorted_aggdata>100]), length.out = paletteLength*(max(sorted_aggdata))/10)
myBreaks_last <- c(myBreaks_below, myBreaks_above)

myBreaks<-append(myBreaks_first,myBreaks_last[which(myBreaks_last>max(myBreaks_first))])
myBreaks<-append(myBreaks_first[which(myBreaks_first<min(myBreaks))], myBreaks)
myBreaks<-append(myBreaks_last[which(myBreaks_last<min(myBreaks))], myBreaks)
myBreaks<-append(myBreaks,myBreaks_last[which(myBreaks_last>max(myBreaks))])

myColorbelow<-colorRampPalette(c("blue","white"))(length(which(myBreaks<100))) ### change for white 
myColorabove<-colorRampPalette(c("white","red"))(length(which(myBreaks>100)))### change for white
myColor<-c(myColorbelow, myColorabove)

pdf(file =here("Supplement/Figures/synth_errorduplets_heatmap.pdf"),width=12,height=8, onefile=FALSE)
pheatmap(sorted_aggdata, color=myColor, breaks=myBreaks, main = "Duplets", cluster_cols = FALSE, cluster_rows = FALSE)
dev.off()

pdf(file =here("Supplement/Figures/synth_errorduplets_bar.pdf"),width=12,height=8, onefile=FALSE)
ggplot(melt(t(sorted_aggdata)), aes(x=Var2, y = value, fill = Var1)) + geom_bar(stat = "identity")+facet_grid(~Var1)+theme(legend.position="none")+coord_cartesian(ylim=c(min(myBreaks-10), max(myBreaks+10)))
dev.off()

errorplot <-error
errorplot$duplets <-factor(error$duplets)
pdf(file =here("Supplement/Figures/synth_errorduplets_box.pdf"),width=12,height=8, onefile=FALSE)
ggplot(data = melt(errorplot), aes(x=duplets, y = value, fill = variable)) + geom_boxplot(varwidth = TRUE)+facet_grid(~variable)+theme(legend.position="none")+ geom_smooth(method = "loess", se=TRUE, color="black", aes(group=1, fill = variable)) + theme(axis.text.x = element_text(angle =60, hjust = 1))
dev.off()
table(round(seqs$FoldG))

```

TTTT
```{r}
errorData_toplot<-log2(miRge_synth+1)
errorData_toplot<-(errorData_toplot /colMeans(errorData_toplot))*100

error<-as.data.frame(cbind(TTTT, errorData_toplot))
colnames(error) <- c("TTTT", "Clontech", "Illumina", "NEB", "NEXTflex", "Deduped", "Fivepercent")

aggdata <-aggregate(error[2:7], by=list(error$TTTT), FUN=mean)
rownames(aggdata) <- aggdata$Group.1
aggdata<-aggdata[which(colnames(aggdata)!="Group.1"&colnames(aggdata)!="FoldG")]
sorted_aggdata <-aggdata
paletteLength <- 10

myBreaks_below<-seq(to=max(sorted_aggdata[sorted_aggdata<100]), from = round(min(sorted_aggdata))-3, length.out = paletteLength*abs(min(sorted_aggdata))/10)

myBreaks_above<-seq(to=round(max(sorted_aggdata))+3, from = min(sorted_aggdata[sorted_aggdata>100]), length.out = paletteLength*(max(sorted_aggdata))/10)
myBreaks_last <- c(myBreaks_below, myBreaks_above)

myBreaks<-append(myBreaks_first,myBreaks_last[which(myBreaks_last>max(myBreaks_first))])
myBreaks<-append(myBreaks_first[which(myBreaks_first<min(myBreaks))], myBreaks)
myBreaks<-append(myBreaks_last[which(myBreaks_last<min(myBreaks))], myBreaks)
myBreaks<-append(myBreaks,myBreaks_last[which(myBreaks_last>max(myBreaks))])

myColorbelow<-colorRampPalette(c("blue","white"))(length(which(myBreaks<100))) ### change for white 
myColorabove<-colorRampPalette(c("white","red"))(length(which(myBreaks>100)))### change for white
myColor<-c(myColorbelow, myColorabove)
pdf(file =here("Supplement/Figures/synth_errorTTTT_heatmap.pdf"),width=12,height=8, onefile=FALSE)
pheatmap(sorted_aggdata, color=myColor, breaks=myBreaks, main = "TTTT", cluster_cols = FALSE, cluster_rows = FALSE)
dev.off()

pdf(file =here("Supplement/Figures/synth_errorTTTT_bar.pdf"),width=12,height=8, onefile=FALSE)
ggplot(melt(t(sorted_aggdata)), aes(x=Var2, y = value, fill = Var1)) + geom_bar(stat = "identity")+facet_grid(~Var1)+theme(legend.position="none")+coord_cartesian(ylim=c(min(myBreaks-10), max(myBreaks+10)))
errorplot <-error
dev.off()
errorplot$TTTT<-factor(error$TTTT)
pdf(file =here("Supplement/Figures/synth_errorTTTT_box.pdf"),width=12,height=8, onefile=FALSE)
ggplot(data = melt(errorplot), aes(x=TTTT, y = value, fill = variable)) + geom_boxplot(varwidth = TRUE)+facet_grid(~variable)+theme(legend.position="none") +geom_smooth(method = "loess", se=TRUE, color="black", aes(group=1, fill = variable)) + theme(axis.text.x = element_text(angle =60, hjust = 1))
dev.off()

table(TTTT)

```

anyC
```{r}
errorData_toplot<-log2(miRge_synth+1)
errorData_toplot<-(errorData_toplot /colMeans(errorData_toplot))*100

error<-as.data.frame(cbind(anyC, errorData_toplot))
colnames(error) <- c("anyC", "Clontech", "Illumina", "NEB", "NEXTflex", "Deduped", "Fivepercent")

aggdata <-aggregate(error[2:7], by=list(error$anyC), FUN=mean)
rownames(aggdata) <- aggdata$Group.1
aggdata<-aggdata[which(colnames(aggdata)!="Group.1"&colnames(aggdata)!="FoldG")]
sorted_aggdata <-aggdata
paletteLength <- 10

myBreaks_below<-seq(to=max(sorted_aggdata[sorted_aggdata<100]), from = round(min(sorted_aggdata))-3, length.out = paletteLength*abs(min(sorted_aggdata))/10)

myBreaks_above<-seq(to=round(max(sorted_aggdata))+3, from = min(sorted_aggdata[sorted_aggdata>100]), length.out = paletteLength*(max(sorted_aggdata))/10)
myBreaks_last <- c(myBreaks_below, myBreaks_above)

myBreaks<-append(myBreaks_first,myBreaks_last[which(myBreaks_last>max(myBreaks_first))])
myBreaks<-append(myBreaks_first[which(myBreaks_first<min(myBreaks))], myBreaks)
myBreaks<-append(myBreaks_last[which(myBreaks_last<min(myBreaks))], myBreaks)
myBreaks<-append(myBreaks,myBreaks_last[which(myBreaks_last>max(myBreaks))])

myColorbelow<-colorRampPalette(c("blue","white"))(length(which(myBreaks<100))) ### change for white 
myColorabove<-colorRampPalette(c("white","red"))(length(which(myBreaks>100)))### change for white
myColor<-c(myColorbelow, myColorabove)

pdf(file =here("Supplement/Figures/synth_erroranyC_heatmap.pdf"),width=12,height=8, onefile=FALSE)
pheatmap(sorted_aggdata, color=myColor, breaks=myBreaks, main = "anyC", cluster_cols = FALSE, cluster_rows = FALSE)
dev.off()
pdf(file =here("Supplement/Figures/synth_erroranyC_bar.pdf"),width=12,height=8, onefile=FALSE)
ggplot(melt(t(sorted_aggdata)), aes(x=Var2, y = value, fill = Var1)) + geom_bar(stat = "identity")+facet_grid(~Var1)+theme(legend.position="none")+coord_cartesian(ylim=c(min(myBreaks-10), max(myBreaks+10)))
dev.off()
errorplot <-error

errorplot$anyC<-factor(error$anyC)
melted <- melt(t(errorplot))
anyC_value <-rep(melted[which(melted$Var1 == "anyC"),]$value, each =6)
melted2 <- melted[which(melted$Var1 != "anyC"),]
melted2$anyC_value <-factor(anyC_value)
pdf(file =here("Supplement/Figures/synth_erroranyC_box.pdf"),width=12,height=8, onefile=FALSE)
melted2$Var2<-NULL
melted2$value<-as.numeric(as.character(melted2$value))
melted2$anyC_value<-factor(melted2$anyC_value, levels = c("0","1","2","3","4","5","6","7","8","9","10","11","12","13"))
ggplot(data = melted2, aes(x=anyC_value, y = value, fill = Var1)) + geom_jitter()+ geom_boxplot(varwidth = TRUE) +facet_grid(~Var1)+theme(legend.position="none")+geom_smooth(method = "loess", se=TRUE, color="black", aes(group=1, fill = Var1)) + theme(axis.text.x = element_text(angle =60, hjust = 1))
dev.off()
table(anyC)

```














Variance Plot
```{r}
library(ggplot2)
library(car)
yGene<-as.matrix(log2(miRge_synth+1))
yGene <-as.matrix(errorData_toplot)

lastStuff<-function(str, n){result <-substr(str,(nchar(str)+1)-n,nchar(str))}
seqs_last <- data.frame(x =lastStuff(str=seqs$RNA, 1))####uncomment to get last n bases
rownames(seqs_last)<-seqs$name
seqs_first <-data.frame(x =strtrim(seqs$RNA, c(1)))###uncomment to get first n bases and comment next line
rownames(seqs_first)<-seqs$name

lastStuff<-function(str, n){result <-substr(str,(nchar(str)+1)-n,nchar(str))}
seqs_last_two <- data.frame(x =lastStuff(str=seqs$RNA, 2))####uncomment to get last n bases
rownames(seqs_last)<-seqs$name
seqs_first_two <-data.frame(x =strtrim(seqs$RNA, c(2)))###uncomment to get first n bases and comment next line
rownames(seqs_first)<-seqs$name

lastStuff<-function(str, n){result <-substr(str,(nchar(str)+1)-n,nchar(str))}
seqs_last_three<- data.frame(x =lastStuff(str=seqs$RNA, 3))####uncomment to get last n bases
rownames(seqs_last)<-seqs$name
seqs_first_three <-data.frame(x =strtrim(seqs$RNA, c(3)))###uncomment to get first n bases and comment next line
rownames(seqs_first)<-seqs$name

lastStuff<-function(str, n){result <-substr(str,(nchar(str)+1)-n,nchar(str))}
seqs_last_four <- data.frame(x =lastStuff(str=seqs$RNA, 4))####uncomment to get last n bases
rownames(seqs_last)<-seqs$name
seqs_first_four <-data.frame(x =strtrim(seqs$RNA, c(4)))###uncomment to get first n bases and comment next line
rownames(seqs_first)<-seqs$name

#seqs$FoldG<-errorFoldG$FoldG
pd<-seqs
pd$First_base <-seqs_first$x
pd$First_2_bases <-seqs_first_two$x
pd$First_3_bases <-seqs_first_three$x
pd$First_4_bases <-seqs_first_four$x
pd$Last_base <-seqs_last$x
pd$Last_2_bases <-seqs_last_two$x
pd$Last_3_bases <-seqs_last_three$x
pd$Last_4_bases <-seqs_last_four$x
pd$TTTT <- TTTT
pd$CCCC <- CCCC
pd$GGGG <- GGGG
pd$AAAA <- AAAA
pd$rep <- (TTTT+ CCCC+ GGGG+ AAAA)
pd$duplets <-duplets
pd$anyT <- anyT
pd$anyC <-anyC
pd$anyG <- anyG
pd$anyA <- anyA


varCompAnalysis = apply(t(yGene),1,function(y) {
  if(runif(1) < 1e-4) cat(".")
  fit = lm(y ~ GC+  + length +FoldG  +First_2_bases + Last_2_bases+ anyA + anyT + anyC + duplets + GGGG + TTTT + CCCC +AAAA , data = pd)
  full =Anova(fit, type = "II")
  fullSS =full$"Sum Sq"
  signif(cbind(full,PctExp=fullSS/
                 sum(fullSS)*100),3)
})



varexp <-do.call(rbind, lapply(varCompAnalysis, data.frame))
labels_varexp <- data.frame(do.call('rbind', strsplit(as.character(rownames(varexp)),'.',fixed=TRUE)))
colnames(labels_varexp)<-c("Kit", "variable")
VarExp<-cbind(labels_varexp,varexp$PctExp)
VarExp$KitF <- factor(VarExp$Kit,levels = c("Clontech", "Illumina", "NEB", "NEXTflex", "Deduped", "Fivepercent"), ordered = TRUE)


variance <- lapply(log2(miRge_synth+1), var)
boxplot(variance)
expression <-log2(miRge_synth+1)

VarExp[which(VarExp$variable == "First_base"),]
VarExp[which(VarExp$variable == "Last_base"),]
VarExp[grep("First", VarExp$variable),]
VarExp[grep("Last", VarExp$variable),]



var_Table <-read.table(here("Var_exp_Table"))
rank_Table <-sapply((-1*var_Table), rank )
```


```{r, eval=TRUE}
library(pheatmap)
varexp2 <-do.call(cbind, lapply(varCompAnalysis, data.frame))
varexp_PctExp<-varexp2[grep("PctExp", colnames(varexp2))]
colnames(varexp_PctExp) <- c("Clontech","Illumina","NEB","NEXTflex","Deduped", "Fivepercent")
varexp_PctExp<- varexp_PctExp[-grep("Residuals",rownames(varexp_PctExp)),]
pdf(file =here("Figures/Raw_plots/Fig.4.c.pdf"),width=3,height=7, onefile = FALSE)
pheatmap(varexp_PctExp, main = "Percent of sequence detection variance explained", cluster_cols = FALSE, cluster_rows = FALSE)
dev.off()
varexp_PctExp2<-((varexp_PctExp*variance)/mean(unlist(variance)))
pdf(file =here("Figures/Raw_plots/Fig.4.d.pdf"),width=3,height=7, onefile=FALSE)
pheatmap(varexp_PctExp2, main = "Percent of sequence detection variance explained \n weighted by overall varaince for each kit", cluster_rows = FALSE, cluster_cols = FALSE)
dev.off()
```

Radar plot of variance

```{r}
library(fmsb)
data=as.data.frame(matrix( sample( 2:20 , 10 , replace=T) , ncol=10))
colnames(data)=c("math" , "english" , "biology" , "music" , "R-coding", "data-viz" , "french" , "physic", "statistic", "sport" )
 
# To use the fmsb package, I have to add 2 lines to the dataframe: the max and min of each topic to show on the plot!
data=rbind(rep(20,10) , rep(0,10) , data)
 
# The default radar chart proposed by the library:
radarchart(data)
 
# Custom the radarChart !
radarchart( data  , axistype=1 , 
 
    #custom polygon
    pcol=rgb(0.2,0.5,0.5,0.9) , pfcol=rgb(0.2,0.5,0.5,0.5) , plwd=4 , 
 
    #custom the grid
    cglcol="grey", cglty=1, axislabcol="grey", caxislabels=seq(0,20,5), cglwd=0.8,
 
    #custom labels
    vlcex=0.8 
    )
Variance<-t(data.frame(unlist(variance)))
var_data <-data.frame(rbind(rep(12,6), rep(0,6), Variance))
radarchart(var_data)

# Custom the radarChart !
radarchart( var_data  , axistype=1 , 
 
    #custom polygon
    pcol=rgb(0.2,0.5,0.5,0.9) , pfcol=rgb(0.2,0.5,0.5,0.5) , plwd=4 , 
 
    #custom the grid
    cglcol="grey", cglty=1, axislabcol="grey", caxislabels=seq(0,20,2), cglwd=0.8,
 
    #custom labels
    vlcex=0.8 
    )
boxplot(Variance)


vplot <- ggplot(data=melt(Variance), aes(x=Var2, y=value, fill = Var2)) +
       geom_bar(position="dodge",stat="identity") +
       ylab("Variance") + 
       xlab(" ")+
       ggtitle("Variance of Synthetic miRNA Detection")+
theme(axis.title.x = element_text(size =0), 
        plot.title = element_text(size = 18, face = "bold", hjust = 0.1), 
        axis.text.x = element_text(size = 18, angle =45, color = "black", vjust = 0.6),
        axis.text.y = element_text(size = 20), 
        axis.title.y = element_text(size =18))

pdf(file =here("Figures/Raw_plots/Fig.4.b.pdf"),width=6,height=4)
vplot    +  theme(legend.position = "none") + geom_text(aes(label = (round(value, digits =2)), size = 5, hjust = 0.5, vjust = 1.5) )
dev.off()
```

