---
title: "Repro_1000_all_files_May7"
author: "Carrie Wright"
date: "5/7/2018"
output: html_document
---

```{r, eval=TRUE, echo=FALSE}
library(edgeR)
library(here)

Pheno<- read.table(here("18seed15limALLfiles/Pheno.csv"), header = T, sep = ",")
Pheno1000 <- Pheno[which(Pheno$startingAmt =="1000"),]#grab just the 1000ng samples

miR_counts<-read.table(here("18seed15limALLfiles/miR.Counts.csv"), header = TRUE, sep = ",")
rownames(miR_counts)<- miR_counts$miRNA#make miRNA rownames
miR_counts<-miR_counts[,2:length(colnames(miR_counts))]#remove miRNA col
miRNAtotal<-t(miR_counts[1,])#extract the total miRNA counts... in case we want them
miR_counts<-miR_counts[-1,]#remove total miRNA counts row
miR_counts<- miR_counts[which(Pheno$startingAmt=="1000")]#grab just the 1000ng samples

colnames(miR_counts)<-gsub("directional_dedupped|directional_deduped", "Deduped", colnames(miR_counts))
colnames(miR_counts)<-gsub("NEXT_", "NEXTflex_", colnames(miR_counts))

###To get rid of extra files
Pheno1000<-Pheno1000[-c(13:18),]
miR_counts<-miR_counts[-c(13:18)]

##To get rid of extra kits
miR_counts<-miR_counts[-which(Pheno1000$Kit =="NEXTflex" |Pheno1000$Kit=="Fivepercent")]
Pheno1000<-Pheno1000[-which(Pheno1000$Kit =="NEXTflex" |Pheno1000$Kit=="Fivepercent"),]



#Pheno1000$Kit<-gsub("NEXTflex_directional_deduped", "Deduped", Pheno1000$Kit)
# Pheno1000$Kit<-gsub("NEXTflex_Fivepercent", "Fivepercent", Pheno1000$Kit)
# Pheno1000$TriplicateGroup<-gsub("NEXTflex_directional_deduped", "Deduped", Pheno1000$TriplicateGroup)
# Pheno1000$TriplicateGroup<-gsub("NEXTflex_Fivepercent", "Fivepercent", Pheno1000$TriplicateGroup)
# colnames(miR_counts)<-gsub("directional_deduped_lib_align_seed15", "Deduped", colnames(miR_counts))
# colnames(miR_counts)<-gsub("NEXTflex_Fivepercent", "Fivepercent", colnames(miR_counts))

miR_1000_raw <-miR_counts
Pheno <-Pheno1000

#miR_1000_raw <- miR_1000_raw[-which(Pheno$Kit=="Fivepercent")]
#Pheno <- Pheno[-which(Pheno$Kit=="Fivepercent"),]

library(ggplot2)
# gg_color_hue <- function(n) {
#   hues = seq(15, 375, length = n + 1)
#   hcl(h = hues, l = 65, c = 100)[1:n]
# }
# n = 6
# cols = gg_color_hue(n)
# cols <-c(cols[1:4], cols[6], cols[5])


gg_color_hue <- function(n) {
  hues = seq(15, 375, length = n + 1)
  hcl(h = hues, l = 65, c = 100)[1:n]
}
n = 65
cols = gg_color_hue(n)
#cols <-c(cols[1:4], cols[6], cols[5])

#load("/Users/carriewright/Documents/miRNA seq Projects/miRNA_kit_comparison_project/DATA_ANALYSIS/UnionInfo.rda")
```

###DESeq2
```{r, eval=FALSE, warning=FALSE, message=FALSE, echo =FALSE}
library(DESeq2)
dds<-DESeqDataSetFromMatrix(countData = miR_1000_raw, colData = Pheno, design = ~ Kit)
dds <- estimateSizeFactors(dds)
norm_miR_1000<-data.frame(counts(dds, normalized = TRUE))
dim(norm_miR_1000)
```
###TMM Normalization

```{r, eval= TRUE, echo =FALSE}
library(edgeR)
group <-Pheno$Kit
d<-DGEList(counts = miR_1000_raw, group = group)
miR_1000_TMM_edgeR_factors <-calcNormFactors(d, method = "TMM")
TMM <-estimateCommonDisp(miR_1000_TMM_edgeR_factors)
norm_miR_1000 <-data.frame(TMM$pseudo.counts)
dim(norm_miR_1000)
```


```{r}
###split the data by kit
split_kit <- list() 
for(i in Pheno$Kit) { 
  split_kit[[i]] <- data.frame(norm_miR_1000[which(Pheno$Kit==i)])
} 

###split the data by kit and batch
split_batch <- list() 
for(i in Pheno$TriplicateGroup) { 
  split_batch[[i]] <- data.frame(norm_miR_1000[which(Pheno$TriplicateGroup==i)])
}
```

```{r}
###genefilter
library(genefilter)
poverafun <- genefilter::pOverA(p = 1, A = 10)#at least 100 normalized reads in all samples of the set... 

ffun <- filterfun(poverafun)
genefilt_fun<- function(x){genefilter(x, ffun)}
thresh<-lapply(split_kit, genefilt_fun)

split_kit_thresh <-list()
split_kit_thresh$Clontech<-split_kit$Clontech[thresh$Clontech,]
split_kit_thresh$Illumina<-split_kit$Illumina[thresh$Illumina,]
split_kit_thresh$NEB<-split_kit$NEB[thresh$NEB,]
#split_kit_thresh$NEXTflex<-split_kit$NEXTflex[thresh$NEXTflex,]
split_kit_thresh$Double<-split_kit$Double[thresh$Double,]
split_kit_thresh$Deduped<-split_kit$Deduped[thresh$Deduped,]
#split_kit_thresh$Fivepercent<-split_kit$Fivepercent[thresh$Fivepercent,]




thresh<-lapply(split_batch, genefilt_fun)


split_batch_thresh <-list()
split_batch_thresh$Clontech1000_Batch1<-split_batch$Clontech1000_Batch1[thresh$Clontech1000_Batch1,]
split_batch_thresh$Clontech1000_Batch2<-split_batch$Clontech1000_Batch2[thresh$Clontech1000_Batch2,]
split_batch_thresh$Illumina1000_Batch1<-split_batch$Illumina1000_Batch1[thresh$Illumina1000_Batch1,]
split_batch_thresh$Illumina1000_Batch2<-split_batch$Illumina1000_Batch2[thresh$Illumina1000_Batch2,]
split_batch_thresh$NEB1000_Batch1<-split_batch$NEB1000_Batch1[thresh$NEB1000_Batch1,]
split_batch_thresh$NEB1000_Batch2<-split_batch$NEB1000_Batch2[thresh$NEB1000_Batch2,]
#split_batch_thresh$NEXTflex1000_Batch1<-split_batch$NEXTflex1000_Batch1[thresh$NEXTflex1000_Batch1,]
#split_batch_thresh$NEXTflex1000_Batch2<-split_batch$NEXTflex1000_Batch2[thresh$NEXTflex1000_Batch2,]
split_batch_thresh$Double1000_Batch1 <-split_batch$Double1000_Batch1[thresh$Double1000_Batch1,]
split_batch_thresh$Double1000_Batch2<-split_batch$Double1000_Batch2[thresh$Double1000_Batch2,]
split_batch_thresh$Deduped1000_Batch1<-split_batch$Deduped1000_Batch1[thresh$Deduped1000_Batch1,]
split_batch_thresh$Deduped1000_Batch2<-split_batch$Deduped1000_Batch2[thresh$Deduped1000_Batch2,]
#split_batch_thresh$Fivepercent1000_Batch1<-split_batch$Fivepercent1000_Batch1[thresh$Fivepercent1000_Batch1,]
#split_batch_thresh$Fivepercent1000_Batch2<-split_batch$Fivepercent1000_Batch2[thresh$Fivepercent1000_Batch2,]



split_batch_thresh_batch1 <- split_batch_thresh[grep("Batch1", names(split_batch_thresh))]
split_batch_thresh_batch2 <- split_batch_thresh[grep("Batch2", names(split_batch_thresh))]
```


```{r}
###The Function
library(limma)
library(edgeR)

single <- function(kit) {
  dat<-split_kit_thresh[grep(kit, names(split_kit_thresh))]
  dat<-data.frame(dat)
  p <- Pheno[grep(kit, (Pheno[, 2])), ]
  design <- model.matrix(~p$Batch)
  data_s <<- log2(dat + 1)
  f <- lmFit(data_s, design)
  f <- eBayes(f)
}
```

```{r}
kits<-as.character(unique(Pheno$Kit))
fits <-lapply(kits, single)
names(fits) <-kits
```

Evaluate Batch P values
```{R, eval = TRUE}
##########pvalues etc.#####
pval_single <-list()
pval_single<-lapply(fits, function(f) { f$p.value[, 2] })
pval_df_single <-lapply(pval_single, data.frame)
qval_single <- sapply(pval_single, p.adjust, method = 'fdr')
qval_df_single <-lapply(qval_single, data.frame)


raw_table<-sapply(qval_df_single, function(x) { table(x > 0.05 )}) # TRUE = not sig accross batch is true
raw_table
percent_table_noBatcheffect<-(raw_table[which(rownames(raw_table) == "TRUE"),] / colSums(raw_table))*100
percent_table_Batcheffect<-(raw_table[which(rownames(raw_table) == "FALSE"),] / colSums(raw_table))*100
#round(sapply(qval_df_single, function(x) { table(x > 0.05 )}) / nrow(qval_df_single) * 100, 2)

```

###Paired Test
```{r, echo = FALSE, message = FALSE, eval = TRUE}
library(dplyr)

Names_thresh<-(intersect(intersect(intersect(intersect(rownames(split_kit_thresh[[1]]), rownames(split_kit_thresh[[2]])), rownames(split_kit_thresh[[3]])), rownames(split_kit_thresh[[4]])), rownames(split_kit_thresh[[5]])))

#Names_thresh<-intersect(intersect(intersect(intersect(intersect(rownames(split_kit_thresh[[1]]), rownames(split_kit_thresh[[2]])), rownames(split_kit_thresh[[3]])), rownames(split_kit_thresh[[4]])), rownames(split_kit_thresh[[5]])), rownames(split_kit_thresh[[6]]))

#Names_thresh<-intersect(intersect(intersect(intersect(intersect(intersect(rownames(split_kit_thresh[[1]]), rownames(split_kit_thresh[[2]])), rownames(split_kit_thresh[[3]])), rownames(split_kit_thresh[[4]])), rownames(split_kit_thresh[[5]])), rownames(split_kit_thresh[[6]])), rownames(split_kit_thresh[[7]]))

finding_rows<-function(x){x[rownames(x) %in% Names_thresh,]}

qvals <- lapply(qval_df_single, finding_rows)  
qvals <- data.frame(qvals)
colnames(qvals)<-names(qval_df_single)
#qvals <- -log10(qvals)
  test_names <- data.frame(combn(kits, m= 2))

get_test_results<- function(data,test_names, pairedvalue) {
  tresults<<-list()
  tested_names1<<-list()
  tested_names2<<-list()
  for(i in names(test_names)){
    Kit1 <-data[which(names(data) %in% test_names[i][1,])]
    Kit2 <-data[which(names(data) %in% test_names[i][2,])]
    Kit1<-data.frame(select(data, colnames(data)[colnames(data) %in% test_names[i][1,]]))
    Kit2<-data.frame(select(data, colnames(data)[colnames(data) %in% test_names[i][2,]]))
    tested_names1[[i]]<<-names(data)[names(data) %in% test_names[i][1,]]
    tested_names2[[i]]<<-names(data)[names(data) %in% test_names[i][2,]]
    colnames(Kit1)<-c("error")
    colnames(Kit2)<-c("error")
    tresults[[i]]<<-t.test(x=Kit1[[1]], y=Kit2[[1]], paired = pairedvalue)
    tested_kits <<-paste0(tested_names1, "&", tested_names2)
  }
}

get_ttestStats<- function(x, tested_kits) {
  c(t =format(x$statistic, digits = 2),
    df = format(x$parameter, digits = 0),
    p.value = format(x$p.value, scientific = TRUE, digits = 2),
    bonferroni.threshold = format(.05/length(test_names), digits = 2),
    sig = ifelse(x$p.value<(.05/length(test_names)), "yes", "no"))
}
```

in this case... a lower t is worse... because we are using the qvals for batch effect significance
```{r, eval = TRUE}
#get_test_names(qval_df_single, eval = FALSE)
get_test_results(data = qvals, test_names = test_names, pairedvalue = TRUE)
ttestStats_across<-data.frame(lapply(tresults, get_ttestStats, tested_kits = tested_kits))
colnames(ttestStats_across)<-tested_kits
ttestStats_across
```

Accross Batch Error Plot
```{r, eval=TRUE}
library(ggplot2)
library(reshape2)



qvals <- -log10(qvals)



make_plot <- function(qvals, coef = FALSE) {
qvals$variable <- factor(qvals$variable, levels =c("Clontech","Illumina","NEB","Double", "Deduped"))
    plot1001<-ggplot(data = qvals, aes(x = variable, y = value, color= variable))+geom_jitter(alpha =0.7) +geom_jitter(outlier.shape = NA, varwidth = TRUE)+
      ggtitle(label = "Inconsistency Across Batch")+ 
      labs(y = ifelse(coef, "Coef for batch effect \n on indv. miRNAs", "-log10(q) for batch effect \n on indv. miRNAs"))+
      theme(axis.title.x = element_text(size =0), 
            plot.title = element_text(size = 30, face = "bold", hjust = 0.5), 
            axis.text.x = element_text(size = 10),
            axis.text.y = element_text(size = 20), 
            axis.title.y = element_text(size =15),
            legend.position= "none") 
    plot1001
    
    
    
    #+scale_fill_manual(values=kit_colors)+ scale_color_manual(values=rep("black", 5)) #+geom_jitter(aes(fill = variable, alpha =.3))+scale_fill_manual(values=kit_colors)+ scale_color_manual(values=rep("black", 5))
    
    plot1001  +scale_fill_manual(values=cols)+ scale_color_manual(values=rep("black", 6)) + geom_point() + scale_color_manual(values=cols) + geom_boxplot(alpha =0.7)
    plot1001  +scale_fill_manual(values=cols)+ scale_color_manual(values=rep("black", 6)) + geom_point() + scale_color_manual(values=cols)+ geom_boxplot(alpha =0.7,outlier.shape = NA)
}

make_plot(qvals =melt((qvals)))



```


###Evaluate Within Batch Error Function#
```{r, echo=TRUE, message=FALSE, warning=FALSE, eval = TRUE}

library(reshape2)
library(limma)
library(edgeR)
library(dplyr)


test_names <- data.frame(combn(Pheno$TriplicateGroup, m= 2))
  
get_error<- function(data) {
  errorData <<-list()
  errordata <<-data.frame()
  #error_for_graph <<-list()
  for(i in names(data)){
  data_kit <<-data.frame(data[grep(i,names(data))])
  errordata <-data_kit - rowMeans(data_kit)
  errordata <-abs(errordata)
  #error_for_graph<<-melt(errordata)
  errordata <-log2(errordata +1)
  errorData[[i]]<<-errordata
  }
}

```

Higher t is worse = higher error

###Within Error Batch 1 
```{r}
get_error(data = split_batch_thresh_batch1)

mean_errors_1 <- lapply(errorData, rowMeans)


test_names <- data.frame(combn(names(split_batch_thresh_batch1), m= 2))

errorData_test <-lapply(mean_errors_1, data.frame)
errorData_test <- lapply(errorData_test, finding_rows)  
errorData_test <- data.frame(errorData_test)
colnames(errorData_test) <-names(split_batch_thresh_batch1)

get_test_results(data = errorData_test, test_names = test_names, pairedvalue = TRUE)
#get_test_results(data = mean_errors_1, test_names = test_names)

ttestStats_within_1<-data.frame(lapply(tresults, get_ttestStats, tested_kits = tested_kits))
colnames(ttestStats_within_1)<-tested_kits
ttestStats_within_1

```

###Within Error Plots Batch 1###########
```{r, echo=FALSE, warning=FALSE, eval=TRUE}
library(ggplot2)

melted_errordata_1 <- melt(errorData_test)
Within_error_df <- melted_errordata_1
Within_error_df$variable<-gsub("1000_Batch1", "", Within_error_df$variable)

make_plot <- function(Within_error_df) {
   #Within_error_df$variable <- factor(Within_error_df$variable, levels =c("Clontech","Illumina","NEB","NEXTflex","Double", "Deduped","Fivepercent"))
    Within_error_df$variable <- factor(Within_error_df$variable, levels =c("Clontech","Illumina","NEB","Double", "Deduped"))
    #Within_error_df$variable <- factor(Within_error_df$variable, levels =c("Clontech","Illumina","NEB","NEXTflex","Deduped"))
  plot1000<<-ggplot(data = melt(Within_error_df), aes(x = variable, y = value, color= variable)) +geom_jitter(aes(color = variable, alpha =.7)) +
  theme(axis.title.x = element_text(size =0), 
        plot.title = element_text(size = 18, face = "bold", hjust = 0.1), 
        axis.text.x = element_text(size = 10),
        axis.text.y = element_text(size = 10), 
        axis.title.y = element_text(size =18))
}
make_plot(Within_error_df = Within_error_df)

# if you want the original plot colors :
#plot1000 +scale_color_manual(values=kit_colors) + theme(legend.position = "none") + labs(y = "Absolute error from the mean", title = "Within batch error across kits in first batch") + ylim(0,10000)

# if you want boxplot : +geom_boxplot(aes(fill = L1, alpha =.7), outlier.shape = NA)

plot1000  + theme(legend.position = "none") + labs(y = "Absolute error from the mean", title = "Within batch error across kits in first batch") + geom_boxplot(varwidth = TRUE, outlier.shape = NA)
```
###Within Error Batch 2
```{r}
get_error(data = split_batch_thresh_batch2)

mean_errors_2 <- lapply(errorData, rowMeans)
melted_errordata_2 <- melt(errorData)


test_names <- data.frame(combn(names(split_batch_thresh_batch2), m= 2))

errorData_test <-lapply(mean_errors_2, data.frame)
errorData_test <- lapply(errorData_test, finding_rows)  
errorData_test <- data.frame(errorData_test)
colnames(errorData_test) <-names(split_batch_thresh_batch2)

get_test_results(data = errorData_test, test_names = test_names, pairedvalue = TRUE)
#get_test_results(data = mean_errors_2, test_names = test_names)

ttestStats_within_2<-data.frame(lapply(tresults, get_ttestStats, tested_kits = tested_kits))
colnames(ttestStats_within_2)<-tested_kits
ttestStats_within_2


```

###Within Error Plots Batch 2###########
```{r, echo=FALSE, warning=FALSE, eval=TRUE}
library(ggplot2)


melted_errordata_2 <- melt(errorData_test)
Within_error_df <- melted_errordata_2
Within_error_df$variable<-gsub("1000_Batch2", "", Within_error_df$variable)

# make_plot(Within_error_df = Within_error_df)
# plot1000 +scale_fill_manual(values=kit_colors) + theme(legend.position = "none") + labs(y = "Absolute error from the mean", title = "Within batch error across kits in second batch") + ylim(0,10000)

make_plot(Within_error_df = Within_error_df)
plot1000 + theme(legend.position = "none") + labs(y = "Absolute error from the mean", title = "Within batch error across kits in second batch") + geom_boxplot(varwidth = TRUE, outlier.shape = NA)
```
```{r}
ttestStats_within_1
#this time larger t is worse performance - larger error
```

```{r}
ttestStats_within_2
#this time larger t is worse performance - larger error
```




######################
##Mean within error of both batches

```{r, eval = TRUE}

  mean_errors_avg <- list()

get_means <-function(kits) {
  for(i in kits){
  intersection <- rownames(as.data.frame(mean_errors_1[grep(i,  names(mean_errors_1))]))[which(rownames(as.data.frame(mean_errors_1[grep(i, names(mean_errors_1))])) %in% rownames(as.data.frame(mean_errors_2[grep(i, names(mean_errors_2))])))]
   batch1<-as.data.frame(mean_errors_1[grep(i, names(mean_errors_1))])[which(rownames(as.data.frame(mean_errors_1[grep(i, names(mean_errors_1))])) %in% intersection), , drop = FALSE]
   batch2<-as.data.frame(mean_errors_2[grep(i,     names(mean_errors_2))])[which(rownames(as.data.frame(mean_errors_2[grep(i, names(mean_errors_2))])) %in% intersection), , drop = FALSE]
  kit_together<-cbind(batch1, batch2)
  mean_errors_avg[[i]]<<-rowMeans(kit_together)
  }
}


kits <-names(split_kit)
results<-lapply(kits, get_means) 


test_names <- data.frame(combn(names(split_kit), m= 2))

errorData_test <-lapply(mean_errors_avg, data.frame)
errorData_test <- lapply(errorData_test, finding_rows)  
errorData_test <- data.frame(errorData_test)
colnames(errorData_test) <-names(split_kit_thresh)

get_test_results(data = errorData_test, test_names = test_names, pairedvalue = TRUE)

ttestStats_within_avg<-data.frame(lapply(tresults, get_ttestStats, tested_kits = tested_kits))
colnames(ttestStats_within_avg)<-tested_kits

ttestStats_within_avg

```
##mean within error plot
```{r, echo=FALSE, warning=FALSE, eval=TRUE, message=FALSE}
library(ggplot2)

melted_errordata_avg <- melt(errorData_test)
Within_error_df <- melted_errordata_avg
  
make_plot(Within_error_df = Within_error_df)
plot1000  + theme(legend.position = "none") + labs(y = "Absolute error from the mean", title = "Average within batch error across kits")

#plot1000  + theme(legend.position = "none") + labs(y = "Absolute error from the mean", title = "Average within batch error across kits")  + geom_boxplot(varwidth = TRUE, outlier.shape = NA)
```