---
title: "Starting_amount_across_kits"
author: "Carrie Wright"
date: "6/28/2018"
output: html_document
---

###################################################################################

Check the similarity of the data across starting amts for a given kit
###load data into R
```{r, echo=FALSE}
library(here)


#trying the other data out###################
Pheno<- read.table(here("Brain_samples_missingClontech_batch2/Pheno_2.csv"), header = T, sep = ",")
miR_counts <- read.table(here("Brain_samples_missingClontech_batch2/miR.Counts.csv"),header = T, sep = ",")
miRNAtotal <-t(miR_counts[1,])
miRNAtotal <- miRNAtotal[-1,]
miRNAtotal<-data.frame(miRNAtotal)
miR_counts <-miR_counts[-1,]
miR_counts <-miR_counts[-1]

#######################

colnames(miR_counts)<-gsub("directional_dedupped|directional_deduped", "Deduped", colnames(miR_counts))
colnames(miR_counts)<-gsub("NEXT_", "NEXTflex_", colnames(miR_counts))

miR_counts<-miR_counts[,-grep("Accur", Pheno$Batch)]
Pheno<-Pheno[-grep("Accur", Pheno$Batch),]

###split the data by Kit
split_Kit <- list() 
for(i in Pheno$Kit) { 
  split_Kit[[i]] <- data.frame(miR_counts[which(Pheno$Kit==i)])
}
###split the pheno by starting Amount
Pheno_Kit <- list() 
for(i in Pheno$Kit) { 
  Pheno_Kit[[i]] <- data.frame(Pheno[which(Pheno$Kit==i),])
}


```
###DESeq2 normalization across kit for each starting amount
```{r, eval=TRUE, warning=FALSE, message=FALSE, echo =FALSE}
library(DESeq2)
norm_miR <-list()
for(i in unique(Pheno$Kit)){
dds<-DESeqDataSetFromMatrix(countData = split_Kit[[i]], colData = Pheno[which(Pheno$Kit==i),], design = ~ startingAmt)
dds <- estimateSizeFactors(dds)
norm_miR[[i]]<-data.frame(counts(dds, normalized = TRUE))
dim(norm_miR)
}
```


###Filter the data across triplicates for given kit at a given amount
```{r}
###genefilter
library(genefilter)

poverafun <- genefilter::pOverA(p = 1, A = 10)#at least 100 normalized reads in all samples of the set... 
ffun <- filterfun(poverafun)
genefilt_fun<- function(x){genefilter(x, ffun)}

thresh<-lapply(norm_miR, genefilt_fun)


#test <-split_norm_Kit$Clontech$starting_amt_1000[thresh$Clontech$starting_amt_1000,]

split_kit_thresh <-list()
for(kit in names(norm_miR)){
 split_kit_thresh[[kit]]<- norm_miR[[kit]][thresh[[kit]],]}


split_kit_Amt <- list() 
for(kit in names(split_kit_thresh)){
  for(amt in as.character(unique(Pheno_Kit[[kit]]$startingAmt))){
  split_kit_Amt[[kit]][[amt]] <-split_kit_thresh[[kit]][which(Pheno_Kit[[kit]]$startingAmt == amt)]}
}
#str(split_norm_Amt)

```


consistency of results for each kit across amounts

```{r, echo=TRUE, message=FALSE, warning=FALSE, eval = TRUE}

library(reshape2)
library(limma)
library(edgeR)
library(dplyr)


get_test_results<- function(data,test_names, pairedvalue) {
  tresults<<-list()
  tested_names1<<-list()
  tested_names2<<-list()
  for(i in names(test_names)){
    Kit1 <-data[which(names(data) %in% test_names[i][1,])]
    Kit2 <-data[which(names(data) %in% test_names[i][2,])]
    #Kit1<-data.frame(select(data, colnames(data)[colnames(data) %in% test_names[i][1,]]))
    #Kit2<-data.frame(select(data, colnames(data)[colnames(data) %in% test_names[i][2,]]))
    tested_names1[[i]]<<-names(data)[names(data) %in% test_names[i][1,]]
    tested_names2[[i]]<<-names(data)[names(data) %in% test_names[i][2,]]
    #colnames(Kit1)<-c("error")
    #colnames(Kit2)<-c("error")
    tresults[[i]]<<-t.test(x=Kit1[[1]], y=Kit2[[1]], paired = pairedvalue)
    tested_kits <<-paste0(tested_names1, "&", tested_names2)
  }
}

get_ttestStats<- function(x, tested_kits) {
  c(t =format(x$statistic, digits = 2),
    df = format(x$parameter, digits = 0),
    p.value = format(x$p.value, scientific = TRUE, digits = 2),
    bonferroni.threshold = format(.05/length(test_names), digits = 2),
    sig = ifelse(x$p.value<(.05/length(test_names)), "yes", "no"))
}


get_error<- function(data) {
  for(i in names(data)){
  data_kit <-data[which(names(data) ==i)]
  data_kit <-as.data.frame(data_kit[[1]])
  errordata <-data_kit - rowMeans(data_kit)
  errordata <-abs(errordata)
  #error_for_graph<<-melt(errordata)
  errordata <-log2(errordata +1)
  errorData[[i]]<<-errordata
  }
}

gg_color_hue <- function(n) {
  hues = seq(15, 375, length = n + 1)
  hcl(h = hues, l = 65, c = 100)[1:n]
}

n = 6
cols = gg_color_hue(n)


#finding_rows<-function(x){x[rownames(x) %in% Names_thresh, , drop= FALSE]}

```

###Within Error Clontech
```{r}
amts <-names(split_kit_Amt$Clontech)
tested_data <- split_kit_Amt$Clontech
test_names <- data.frame(combn(amts, m= 2))

    errorData <-list()
    errordata <-data.frame()
get_error(data = tested_data)
mean_errors_1 <- lapply(errorData, rowMeans)

errorData_test <-data.frame(mean_errors_1)
#errorData_test <-lapply(mean_errors_1, data.frame)
colnames(errorData_test) <-names(tested_data)
get_test_results(data = errorData_test, test_names = test_names, pairedvalue = TRUE)
ttestStats_within_1<-data.frame(lapply(tresults, get_ttestStats, tested_kits = tested_kits))
colnames(ttestStats_within_1)<-tested_kits
ttestStats_within_1

```

###Within Error Clontech Plot#
```{r, echo=FALSE, warning=FALSE}
library(ggplot2)

melted_errordata_1 <- melt(errorData_test)
Within_error_df <- melted_errordata_1
Within_error_df$variable <- as.numeric(as.character(Within_error_df$variable))
fit = lm(Within_error_df$value ~ Within_error_df$variable)
anova(fit)
Within_error_df$variable <- factor(Within_error_df$variable, levels =c("100", "250", "500","1000" ,"1500", "2000"), order = TRUE)

make_plot <- function(Within_error_df) {
  plot1000<<-ggplot(data = melt(Within_error_df), aes(x = variable, y = value)) +geom_jitter(color =cols[1], aes(alpha =.7)) +
  theme(axis.title.x = element_text(size =0), 
        plot.title = element_text(size = 18, face = "bold", hjust = 0.1), 
        axis.text.x = element_text(size = 10),
        axis.text.y = element_text(size = 10), 
        axis.title.y = element_text(size =18))
}
make_plot(Within_error_df = Within_error_df)


plot1000  + theme(legend.position = "none") + labs(y = "Absolute error from the mean", title = "Within batch error across starting amounts for Clontech") + geom_boxplot(varwidth = TRUE, outlier.shape = NA)
```



###Within Error Illumina
```{r}
amts <-names(split_kit_Amt$Illumina)
tested_data <- split_kit_Amt$Illumina
test_names <- data.frame(combn(amts, m= 2))
    errorData <-list()
    errordata <-data.frame()
get_error(data = tested_data)
mean_errors_1 <- lapply(errorData, rowMeans)

errorData_test <-data.frame(mean_errors_1)
#errorData_test <-lapply(mean_errors_1, data.frame)
colnames(errorData_test) <-names(tested_data)
get_test_results(data = errorData_test, test_names = test_names, pairedvalue = TRUE)
ttestStats_within_1<-data.frame(lapply(tresults, get_ttestStats, tested_kits = tested_kits))
colnames(ttestStats_within_1)<-tested_kits
ttestStats_within_1

```

###Within Error IlluminaPlot#
```{r, echo=FALSE, warning=FALSE}
library(ggplot2)
melted_errordata_1 <- melt(errorData_test)
Within_error_df <- melted_errordata_1
Within_error_df$variable <- as.numeric(as.character(Within_error_df$variable))
fit = lm(Within_error_df$value ~ Within_error_df$variable)
anova(fit)
Within_error_df$variable <- factor(Within_error_df$variable, levels =c("1000" ,"1500", "2000"), order = TRUE)

make_plot <- function(Within_error_df) {
  plot1000<<-ggplot(data = melt(Within_error_df), aes(x = variable, y = value)) +geom_jitter(color =cols[2], aes(alpha =.7)) +
  theme(axis.title.x = element_text(size =0), 
        plot.title = element_text(size = 18, face = "bold", hjust = 0.1), 
        axis.text.x = element_text(size = 10),
        axis.text.y = element_text(size = 10), 
        axis.title.y = element_text(size =18))
}
make_plot(Within_error_df = Within_error_df)
plot1000  + theme(legend.position = "none") + labs(y = "Absolute error from the mean", title = "Within batch error across starting amounts for Illumina") + geom_boxplot(varwidth = TRUE, outlier.shape = NA)
```
###Within Error NEB
```{r}
amts <-names(split_kit_Amt$NEB)
tested_data <- split_kit_Amt$NEB
test_names <- data.frame(combn(amts, m= 2))
    errorData <-list()
    errordata <-data.frame()
get_error(data = tested_data)
mean_errors_1 <- lapply(errorData, rowMeans)

errorData_test <-data.frame(mean_errors_1)
#errorData_test <-lapply(mean_errors_1, data.frame)
colnames(errorData_test) <-names(tested_data)
get_test_results(data = errorData_test, test_names = test_names, pairedvalue = TRUE)
ttestStats_within_1<-data.frame(lapply(tresults, get_ttestStats, tested_kits = tested_kits))
colnames(ttestStats_within_1)<-tested_kits
ttestStats_within_1

```
###Within Error NEB Plot#
```{r, echo=FALSE, warning=FALSE}
library(ggplot2)
melted_errordata_1 <- melt(errorData_test)
Within_error_df <- melted_errordata_1
Within_error_df$variable <- as.numeric(as.character(Within_error_df$variable))
fit = lm(Within_error_df$value ~ Within_error_df$variable)
anova(fit)
Within_error_df$variable <- factor(Within_error_df$variable, levels =c("100", "250", "500", "1000"), order = TRUE)


make_plot <- function(Within_error_df) {
  plot1000<<-ggplot(data = melt(Within_error_df), aes(x = variable, y = value)) +geom_jitter(color =cols[3], aes(alpha =.7)) +
  theme(axis.title.x = element_text(size =0), 
        plot.title = element_text(size = 18, face = "bold", hjust = 0.1), 
        axis.text.x = element_text(size = 10),
        axis.text.y = element_text(size = 10), 
        axis.title.y = element_text(size =18))
}
make_plot(Within_error_df = Within_error_df)
plot1000  + theme(legend.position = "none") + labs(y = "Absolute error from the mean", title = "Within batch error across starting amounts for NEB") + geom_boxplot(varwidth = TRUE, outlier.shape = NA)
```

###Within Error NEXTflex
```{r}
amts <-names(split_kit_Amt$NEXTflex)
tested_data <- split_kit_Amt$NEXTflex
test_names <- data.frame(combn(amts, m= 2))
    errorData <-list()
    errordata <-data.frame()
get_error(data = tested_data)
mean_errors_1 <- lapply(errorData, rowMeans)

errorData_test <-data.frame(mean_errors_1)
#errorData_test <-lapply(mean_errors_1, data.frame)
colnames(errorData_test) <-names(tested_data)
get_test_results(data = errorData_test, test_names = test_names, pairedvalue = TRUE)
ttestStats_within_1<-data.frame(lapply(tresults, get_ttestStats, tested_kits = tested_kits))
colnames(ttestStats_within_1)<-tested_kits
ttestStats_within_1

```

###Within Error NEXTflex Plot#
```{r, echo=FALSE, warning=FALSE}
library(ggplot2)
melted_errordata_1 <- melt(errorData_test)
Within_error_df <- melted_errordata_1
Within_error_df$variable <- factor(Within_error_df$variable, levels =c("100","250", "500","1000" ,"1500", "2000"), order = TRUE)
fit = lm(Within_error_df$value ~ Within_error_df$variable)
anova(fit)


make_plot <- function(Within_error_df) {
  plot1000<<-ggplot(data = melt(Within_error_df), aes(x = variable, y = value)) +geom_jitter(color =cols[4], aes(alpha =.7)) +
  theme(axis.title.x = element_text(size =0), 
        plot.title = element_text(size = 18, face = "bold", hjust = 0.1), 
        axis.text.x = element_text(size = 10),
        axis.text.y = element_text(size = 10), 
        axis.title.y = element_text(size =18))
}
make_plot(Within_error_df = Within_error_df)
plot1000  + theme(legend.position = "none") + labs(y = "Absolute error from the mean", title = "Within batch error across starting amounts for NEXTflex") + geom_boxplot(varwidth = TRUE, outlier.shape = NA)
```


###Within Error Deduped
```{r}
amts <-names(split_kit_Amt$Deduped)
tested_data <- split_kit_Amt$Deduped
test_names <- data.frame(combn(amts, m= 2))
    errorData <-list()
    errordata <-data.frame()
get_error(data = tested_data)
mean_errors_1 <- lapply(errorData, rowMeans)

errorData_test <-data.frame(mean_errors_1)
#errorData_test <-lapply(mean_errors_1, data.frame)
colnames(errorData_test) <-names(tested_data)
get_test_results(data = errorData_test, test_names = test_names, pairedvalue = TRUE)
ttestStats_within_1<-data.frame(lapply(tresults, get_ttestStats, tested_kits = tested_kits))
colnames(ttestStats_within_1)<-tested_kits
ttestStats_within_1

```
###Within Error Deduped Plot#
```{r, echo=FALSE, warning=FALSE}
library(ggplot2)
melted_errordata_1 <- melt(errorData_test)
Within_error_df <- melted_errordata_1
Within_error_df$variable <- as.numeric(as.character(Within_error_df$variable))
fit = lm(Within_error_df$value ~ Within_error_df$variable)
anova(fit)
Within_error_df$variable <- factor(Within_error_df$variable, levels =c("100","250", "500","1000" ,"1500", "2000"), order = TRUE)

make_plot <- function(Within_error_df) {
  plot1000<<-ggplot(data = melt(Within_error_df), aes(x = variable, y = value)) +geom_jitter(color =cols[5], aes(alpha =.7)) +
  theme(axis.title.x = element_text(size =0), 
        plot.title = element_text(size = 18, face = "bold", hjust = 0.1), 
        axis.text.x = element_text(size = 10),
        axis.text.y = element_text(size = 10), 
        axis.title.y = element_text(size =18))
}
make_plot(Within_error_df = Within_error_df)
plot1000  + theme(legend.position = "none") + labs(y = "Absolute error from the mean", title = "Within batch error across starting amounts for Deduped") + geom_boxplot(varwidth = TRUE, outlier.shape = NA)
```





###Within Error Fivepercent
```{r}
amts <-names(split_kit_Amt$Fivepercent)
tested_data <- split_kit_Amt$Fivepercent
test_names <- data.frame(combn(amts, m= 2))
    errorData <-list()
    errordata <-data.frame()
get_error(data = tested_data)
mean_errors_1 <- lapply(errorData, rowMeans)

errorData_test <-data.frame(mean_errors_1)
#errorData_test <-lapply(mean_errors_1, data.frame)
colnames(errorData_test) <-names(tested_data)
get_test_results(data = errorData_test, test_names = test_names, pairedvalue = TRUE)
ttestStats_within_1<-data.frame(lapply(tresults, get_ttestStats, tested_kits = tested_kits))
colnames(ttestStats_within_1)<-tested_kits
ttestStats_within_1

```


###Within Error Fivepercent Plot#
```{r, echo=FALSE, warning=FALSE}
library(ggplot2)
melted_errordata_1 <- melt(errorData_test)
Within_error_df <- melted_errordata_1
Within_error_df$variable <- as.numeric(as.character(Within_error_df$variable))
fit = lm(Within_error_df$value ~ Within_error_df$variable)
anova(fit)
Within_error_df$variable <- factor(Within_error_df$variable, levels =c("100","250", "500","1000" ,"1500", "2000"), order = TRUE)


make_plot <- function(Within_error_df) {
  plot1000<<-ggplot(data = melt(Within_error_df), aes(x = variable, y = value)) +geom_jitter(color =cols[6], aes(alpha =.7)) +
  theme(axis.title.x = element_text(size =0), 
        plot.title = element_text(size = 18, face = "bold", hjust = 0.1), 
        axis.text.x = element_text(size = 10),
        axis.text.y = element_text(size = 10), 
        axis.title.y = element_text(size =18))
}
make_plot(Within_error_df = Within_error_df)
plot1000  + theme(legend.position = "none") + labs(y = "Absolute error from the mean", title = "Within batch error across starting amounts for Fivpercent") + geom_boxplot(varwidth = TRUE, outlier.shape = NA)
```

